---
title: "generate_plots_model_results"
output: html_document
date: "2023-08-16"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(tidyr)
#library(tidyverse)
library(ggplot2)
library(gridExtra)
library(dplyr)
library(data.table)

library(ggsci) # For publishing group-specific color scemes
# Link for ggsci tutorial: https://cran.r-project.org/web/packages/ggsci/vignettes/ggsci.html#Continuous_color_palettes
# another ggsci link: https://cran.r-project.org/web/packages/ggsci/vignettes/ggsci.html


# Set wd when not in RStudio
setwd('__PATH HERE__')


# Includes AHRQ data. 

df_2_baseline_sg_results <- read.csv("../scripts/__ model results CSV file __")


```


# Baseline general model: To check which model performs with the highest AUC on average overall...
(out of RF, xgboost, MLP, logistic)
```{r}
# Across all feats & subgroups.
avg_auc <- df_2_baseline_sg_results %>% group_by(model) %>% summarise(mean_auc = mean(auc)) %>% arrange(model, desc(mean_auc))
avg_auc <- avg_auc %>% arrange(desc(mean_auc))
avg_auc
# 1st row here is model with HIGHEST mean AUC (among subgroups, feats, and folds.)


med_auc <- df_2_baseline_sg_results %>% group_by(model) %>% summarise(median_auc = median(auc)) %>% arrange(model, desc(median_auc))
med_auc <- med_auc %>% arrange(desc(median_auc))
med_auc
# 1st row here is model with HIGHEST median AUC (among subgroups, feats, and folds.)

# Take mean of auc_sd (auc sd is stdev of auc across 10 folds)

# Take mean of auc_variance. Then take sqrt of final auc_variance. 
# Why: we can take mean of variances, but not stdevs.
stdev_auc <- df_2_baseline_sg_results %>% group_by(model) %>% summarise(std_auc = sqrt(mean(auc_sd^2))) %>% arrange(model, desc(std_auc))
stdev_auc <- stdev_auc %>% arrange(std_auc) # Ascending standard deviation.
stdev_auc
# 1st row here is model with LOWEST stdev of aucs (among subgroups, feats, and folds.)


# Here, adjust 'df_2_baseline_sg_results' to ONLY contain results from "best performing" model according to max avg AUC.
df_2_baseline_sg_results <- df_2_baseline_sg_results[df_2_baseline_sg_results$model == "logr", ]
```



--- Evaluate ONLY Logistic Regression models from here below. (Since logistic got max mean & median AUC).


# To answer question: "DOES EQUITY IN AUC DIFFER BETWEEN FEATURE GROUPS?"
```{r}
# Stratify by feat, then by subgroup.
by_feat_groups <- df_2_baseline_sg_results %>% group_by(feat, subgroup) %>% summarise(max_auc = max(auc)) %>% arrange(feat, desc(max_auc))



# Make subgroup plot
plt_by_feats <- ggplot(
    data = by_feat_groups, 
    aes(x=feat, y=max_auc, group=feat, color=subgroup, group=INDEX, color=INDEX)) +
geom_line() +
  geom_point( position = position_dodge2(
  width = 1,
  preserve = "total",
  padding = 0.1,
  reverse = FALSE

))+
    facet_grid(cols = vars(feat), scales = "free_x", space = "free_x") +
  theme(axis.text.x = element_text(size = 8, angle = 45, hjust = 1), panel.spacing.x = unit(0.001, "cm"),
        strip.text.x = element_blank()) +
scale_color_d3("category20")

plt_by_feats # Show plot



```


# (subset of subgroups) Vertical dot plots
- only on these subgroups:  black, white, male, female, other

```{r}
# First filter for these subgroups only
sgs_selected <- c("black", "white") # c("black", "white", "male", "female", "other")
subset_sgs <- filter(df_2_baseline_sg_results, subgroup %in%  sgs_selected)
# Stratify by feat, then by subgroup.
by_feat_groups <- subset_sgs %>% group_by(feat, subgroup) %>% summarise(mean_auc = auc) %>% arrange(feat, desc(mean_auc))


feat_order <- c( "age_current",
        "sex",
        "demo",
        "hf_vars",
        "comorb",
        "hf_with_comorb",
        "demo_comorb",
        "charlson",
        "hf_with_charlson",

        "adi_national", "adi_state", 
        "sdi", "sdi_score", 
        "svi",
        
        "tot_county_AHRQ_median",
        "tot_county_AHRQ_mean",
        "tot_tract_AHRQ_median",
        "tot_tract_AHRQ_mean",
        
        
        "intersect_county_AHRQ_median",
        "intersect_tract_AHRQ_median"
        
        )

by_feat_groups <- by_feat_groups[by_feat_groups$feat %in% feat_order, ]

by_feat_groups$feat <- factor(by_feat_groups$feat, levels=feat_order)

  

# Make plot
plt_by_feats <- ggplot(
    data = by_feat_groups, 
    aes(x=feat, y=mean_auc, group=feat, color=subgroup, group=INDEX, color=INDEX)) +
geom_line() +
  geom_point( position = position_dodge2(
  width = 1,
  preserve = "total",
  padding = 0.1,
  reverse = FALSE

))+
    facet_grid(cols = vars(feat), scales = "free_x", space = "free_x") +
  theme(axis.text.x = element_text(size = 8, angle = 45, hjust = 1), panel.spacing.x = unit(0.001, "cm"),
        strip.text.x = element_blank()) +
scale_color_d3("category20") 
# + ggtitle("Agnostic Model: Logistic Regression - AHRQ County vs. Tract")

plt_by_feats # Show plot


```


# Experiment 2: Only intersection results
```{r}
# First filter for these subgroups only
sgs_selected <- c("black", "white") # c("black", "white", "male", "female", "other")
subset_sgs <- filter(df_2_baseline_sg_results, subgroup %in%  sgs_selected)
# Stratify by feat, then by subgroup.
by_feat_groups <- subset_sgs %>% group_by(feat, subgroup) %>% summarise(mean_auc = auc) %>% arrange(feat, desc(mean_auc))


feat_order <- c( "age_current",
        "sex",
        "demo",
        "hf_vars",
        "comorb",
        "hf_with_comorb",
        "demo_comorb",
        "charlson",
        "hf_with_charlson",

        "adi_national", "adi_state", 
        "sdi", "sdi_score", 
        "svi",
        
        "intersect_county_AHRQ_median",
        "intersect_tract_AHRQ_median"
        
        )

by_feat_groups <- by_feat_groups[by_feat_groups$feat %in% feat_order, ]

by_feat_groups$feat <- factor(by_feat_groups$feat, levels=feat_order)

  

# Make plot
plt_by_feats <- ggplot(
    data = by_feat_groups, 
    aes(x=feat, y=mean_auc, group=feat, color=subgroup, group=INDEX, color=INDEX)) +
geom_line() +
  geom_point( position = position_dodge2(
  width = 1,
  preserve = "total",
  padding = 0.1,
  reverse = FALSE

))+
    facet_grid(cols = vars(feat), scales = "free_x", space = "free_x") +
  theme(axis.text.x = element_text(size = 8, angle = 45, hjust = 1), panel.spacing.x = unit(0.001, "cm"),
        strip.text.x = element_blank()) +
scale_color_d3("category20") 
# + ggtitle("Agnostic Model: RF - Intersection Features of County vs. Tract")

plt_by_feats # Show plot
```

# Experiment 3 (just air quality imputation methods): Air quality ALONE

```{r}
# First filter for these subgroups only
sgs_selected <- c("black", "white") # c("black", "white", "male", "female", "other")
subset_sgs <- filter(df_2_baseline_sg_results, subgroup %in%  sgs_selected)
# Stratify by feat, then by subgroup.
by_feat_groups <- subset_sgs %>% group_by(feat, subgroup) %>% summarise(mean_auc = auc) %>% arrange(feat, desc(mean_auc))


# Removed: "EPA_AQS_mean", "AHRQ_EPAA_mean",
feat_order <- c( "age_current",
        "sex",
        "demo",
        "hf_vars",
        "comorb",
        "hf_with_comorb",
        "demo_comorb",
        "charlson",
        "hf_with_charlson",

        "adi_national", "adi_state",
        "svi",
        "sdi", 
      
                "tot_county_AHRQ_median",
        
        "EPA_AQS_median",
        "EPA_AQS_spatial",

        "AHRQ_EPAA_median",
        "AHRQ_EPAA_spatial"
        
        )

by_feat_groups <- by_feat_groups[by_feat_groups$feat %in% feat_order, ]

by_feat_groups$feat <- factor(by_feat_groups$feat, levels=feat_order)

  

# RENAME: 
RENAME_cols <- c("Age",
                 "Sex",
                 "Demo",
                 "HF Type",
                 "Comorb",
                 "HF Type+Comorb",
                 "Demo+Comorb",
                 "CCI",
                 "HF Type+CCI",
                 "ADI: National Rank",
                 "ADI: State Rank",
                 "SVI",
                 "SDI",
                 
                 "Total AHRQ: County",
                 "EPA AQS: Median",
                 "EPA AQS: Spatial",
                 "AHRQ EPA: Median",
                 "AHRQ EPA: Spatial"
                  )



rename_map <- setNames(RENAME_cols, feat_order)
by_feat_groups <- by_feat_groups %>% mutate(feat = rename_map[as.character(feat)])

by_feat_groups

# Reorder again
by_feat_groups <- by_feat_groups[by_feat_groups$feat %in% RENAME_cols, ]
by_feat_groups$feat <- factor(by_feat_groups$feat, levels=rev(RENAME_cols))


# Make plot
plt_by_feats <- ggplot(
    data = by_feat_groups, 
    aes(x=mean_auc, y=feat, group=feat, color=subgroup, group=INDEX, color=INDEX)) +
geom_line() +
  geom_point( position = position_dodge2(
  width = 1,
  preserve = "total",
  padding = 0.1,
  reverse = FALSE

))+
  theme(axis.text.x = element_text(size = 8, angle = 45, hjust = 1), panel.spacing.x = unit(0.001, "cm"),
        strip.text.x = element_blank()) +
scale_color_d3("category20") + xlab("AUROC") + ylab("Feature Sets")
  # + ggtitle("SDOHD EPA, EPA AQS imputation methods")

plt_by_feats # Show plot



###############

```


# Experiment 3 (combines SDOHD vars & 2 air quality data sources)
```{r}
# First filter for these subgroups only
sgs_selected <- c("black", "white") # c("black", "white", "male", "female", "other")
subset_sgs <- filter(df_2_baseline_sg_results, subgroup %in%  sgs_selected)
# Stratify by feat, then by subgroup.
by_feat_groups <- subset_sgs %>% group_by(feat, subgroup) %>% summarise(mean_auc = auc) %>% arrange(feat, desc(mean_auc))



feat_order <- c( "age_current",
        "sex",
        "demo",
        "hf_vars",
        "comorb",
        "hf_with_comorb",
        "demo_comorb",
        "charlson",
        "hf_with_charlson",

        "adi_national", "adi_state", 
        "svi",
        "sdi",
        

        "intersect_county_AHRQ_median",
        "intersect_tract_AHRQ_median",

        "intersect_county_AHRQ_median_w_EPAA_spatial",
        "intersect_tract_AHRQ_median_w_EPAA_spatial",

        "intersect_county_AHRQ_median_w_EPA_AQS_spatial",
        "intersect_tract_AHRQ_median_w_EPA_AQS_spatial"

        
        
        )

by_feat_groups <- by_feat_groups[by_feat_groups$feat %in% feat_order, ]

by_feat_groups$feat <- factor(by_feat_groups$feat, levels=feat_order)


# RENAME: 
RENAME_cols <- c("Age",
                 "Sex",
                 "Demo",
                 "HF Type",
                 "Comorb",
                 "HF Type+Comorb",
                 "Demo+Comorb",
                 "CCI",
                 "HF Type+CCI",
                 "ADI: National Rank",
                 "ADI: State Rank",
                 "SVI",
                 "SDI",
                 
                 "Intersection AHRQ: County",
                 "Intersection AHRQ: Tract",
                 
                 "Intersection AHRQ (County) + AHRQ EPA spatial",
                 "Intersection AHRQ (Tract) + AHRQ EPA spatial",
                 
                 "Intersection AHRQ (County) + EPA AQS spatial",
                 "Intersection AHRQ (Tract) + EPA AQS spatial"
                  )



rename_map <- setNames(RENAME_cols, feat_order)
by_feat_groups <- by_feat_groups %>% mutate(feat = rename_map[as.character(feat)])

by_feat_groups

# Reorder again
by_feat_groups <- by_feat_groups[by_feat_groups$feat %in% RENAME_cols, ]
by_feat_groups$feat <- factor(by_feat_groups$feat, levels=rev(RENAME_cols))

  

# Make plot
plt_by_feats <- ggplot(
    data = by_feat_groups, 
    aes(x=mean_auc, y=feat, group=feat, color=subgroup, group=INDEX, color=INDEX)) +
geom_line() +
  geom_point( position = position_dodge2(
  width = 1,
  preserve = "total",
  padding = 0.1,
  reverse = FALSE

))+
  theme(axis.text.x = element_text(size = 8, angle = 45, hjust = 1), panel.spacing.x = unit(0.001, "cm"),
        strip.text.x = element_blank()) +
scale_color_d3("category20") + xlab("AUROC") + ylab("Feature Sets")
  # + ggtitle("") # Agnostic Model: XGBoost - AHRQ + Air Quality

plt_by_feats # Show plot

########

```


# Experiment 4: County & tract intersection (without AHRQ EPAA) *VS.* including EPA_AQS
```{r}
# First filter for these subgroups only
sgs_selected <- c("black", "white") # c("black", "white", "male", "female", "other")
subset_sgs <- filter(df_2_baseline_sg_results, subgroup %in%  sgs_selected)
# Stratify by feat, then by subgroup.
by_feat_groups <- subset_sgs %>% group_by(feat, subgroup) %>% summarise(mean_auc = auc) %>% arrange(feat, desc(mean_auc))



feat_order <- c( "age_current",
        "sex",
        "demo",
        "hf_vars",
        "comorb",
        "hf_with_comorb",
        "demo_comorb",
        "charlson",
        "hf_with_charlson",

        "adi_national", "adi_state", 
        "sdi", "sdi_score", 
        "svi",
        
        "intersect_county_AHRQ_median",
        "intersect_county_AHRQ_median_w_EPA_AQS_spatial"

        )

by_feat_groups <- by_feat_groups[by_feat_groups$feat %in% feat_order, ]

by_feat_groups$feat <- factor(by_feat_groups$feat, levels=feat_order)

  

# Make plot
plt_by_feats <- ggplot(
    data = by_feat_groups, 
    aes(x=feat, y=mean_auc, group=feat, color=subgroup, group=INDEX, color=INDEX)) +
geom_line() +
  geom_point( position = position_dodge2(
  width = 1,
  preserve = "total",
  padding = 0.1,
  reverse = FALSE

))+
    facet_grid(cols = vars(feat), scales = "free_x", space = "free_x") +
  theme(axis.text.x = element_text(size = 8, angle = 45, hjust = 1), panel.spacing.x = unit(0.001, "cm"),
        strip.text.x = element_blank()) +
scale_color_d3("category20") +
  ggtitle("Agnostic Model: XGBoost: AHRQ - EPAA + external EPA")

plt_by_feats # Show plot
```

# Experiment 5: total AHRQ + EPAA or EPA AQS
```{r}
# First filter for these subgroups only
sgs_selected <- c("black", "white") # c("black", "white", "male", "female", "other")
subset_sgs <- filter(df_2_baseline_sg_results, subgroup %in%  sgs_selected)
# Stratify by feat, then by subgroup.
by_feat_groups <- subset_sgs %>% group_by(feat, subgroup) %>% summarise(mean_auc = auc) %>% arrange(feat, desc(mean_auc))



feat_order <- c( "age_current",
        "sex",
        "demo",
        "hf_vars",
        "comorb",
        "hf_with_comorb",
        "demo_comorb",
        "charlson",
        "hf_with_charlson",

        "adi_national", "adi_state", 
        "sdi", "sdi_score", 
        "svi",
        
        
        "county_AHRQ_median_without_EPAA",

        "tot_county_AHRQ_median_without_EPAA_w_EPA_AQS_median",  
        "tot_county_AHRQ_median_without_EPAA_w_EPA_AQS_spatial", 

        "tot_county_AHRQ_median_w_EPAA_w_EPA_AQS_median", 
        "tot_county_AHRQ_median_w_EPAA_w_EPA_AQS_spatial",  
                "tot_county_AHRQ_median_w_EPAA_spatial_w_EPA_AQS_spatial"


        )

by_feat_groups <- by_feat_groups[by_feat_groups$feat %in% feat_order, ]

by_feat_groups$feat <- factor(by_feat_groups$feat, levels=feat_order)

  

# Make plot
plt_by_feats <- ggplot(
    data = by_feat_groups, 
    aes(x=mean_auc, y=feat, group=feat, color=subgroup, group=INDEX, color=INDEX)) +
geom_line() +
  geom_point( position = position_dodge2(
  width = 1,
  preserve = "total",
  padding = 0.1,
  reverse = FALSE

))+
  theme(axis.text.x = element_text(size = 8, angle = 45, hjust = 1), panel.spacing.x = unit(0.001, "cm"),
        strip.text.x = element_blank()) +
scale_color_d3("category20") +
    xlab("AUROC") +
  ylab("Feautre Set") +
  ggtitle("") # Agnostic Model: XGBoost: AHRQ - EPAA + external EPA

plt_by_feats # Show plot


```


# Experiment 6:[COUNTY] AHRQ 5 domains vs. total AHRQ
```{r}
# First filter for these subgroups only
sgs_selected <- c("black", "white") # c("black", "white", "male", "female", "other")
subset_sgs <- filter(df_2_baseline_sg_results, subgroup %in%  sgs_selected)
# Stratify by feat, then by subgroup.
by_feat_groups <- subset_sgs %>% group_by(feat, subgroup) %>% summarise(mean_auc = auc) %>% arrange(feat, desc(mean_auc))

# "tot_county_AHRQ_median",
# "tot_tract_AHRQ_median",

feat_order <- c( "age_current",
        "sex",
        "demo",
        "hf_vars",
        "comorb",
        "hf_with_comorb",
        "demo_comorb",
        "charlson",
        "hf_with_charlson",

        "adi_national", "adi_state",
        "svi",
        "sdi",
        
        "intersect_county_AHRQ_median",
            "intersect_tract_AHRQ_median",
        
        "county_medianIMP_ahrq_1_socialcontext",
                "tract_medianIMP_ahrq_1_socialcontext",

        "county_medianIMP_ahrq_2_economiccontext", 
                    "tract_medianIMP_ahrq_2_economiccontext",

        "county_medianIMP_ahrq_3_education",
                    "tract_medianIMP_ahrq_3_education",

        "county_medianIMP_ahrq_4_physicalinfrastructure",
                    "tract_medianIMP_ahrq_4_physicalinfrastructure",

        "county_medianIMP_ahrq_5_healthcarecontext",
                    "tract_medianIMP_ahrq_5_healthcarecontext"
        )


by_feat_groups <- by_feat_groups[by_feat_groups$feat %in% feat_order, ]
by_feat_groups$feat <- factor(by_feat_groups$feat, levels=feat_order)

  

# "Total AHRQ:                            County",
# "Total AHRQ: Tract",
# RENAME: 
RENAME_cols <- c("Age",
                 "Sex",
                 "Demo",
                 "HF Type",
                 "Comorb",
                 "HF Type+Comorb",
                 "Demo+Comorb",
                 "CCI",
                 "HF Type+CCI",
                 "ADI: National Rank",
                 "ADI: State Rank",
                 "SVI",
                 "SDI",
                 

                 
                  "Intersection AHRQ:                    County",
                  "Intersection AHRQ: Tract",
                 
                 "Domain 1 Social Content: County",
                 "D1: Tract",
                 "Domain 2 Economic Context: County",
                 "D2: Tract",
                 "Domain 3 Education Context: County",
                 "D3: Tract",
                 "Domain 4 Physical Infra.: County",
                 "D4: Tract",
                 "Domain 5 Healthcare Context: County",
                 "D5: Tract"
                  )



rename_map <- setNames(RENAME_cols, feat_order)
by_feat_groups <- by_feat_groups %>% mutate(feat = rename_map[as.character(feat)])

by_feat_groups

# Reorder again
by_feat_groups <- by_feat_groups[by_feat_groups$feat %in% RENAME_cols, ]
by_feat_groups$feat <- factor(by_feat_groups$feat, levels=rev(RENAME_cols))


# Make plot
plt_by_feats <- ggplot(
    data = by_feat_groups, 
    aes(x=mean_auc, y=feat, group=feat, color=subgroup, group=INDEX, color=INDEX)) +
geom_line() +
  geom_point( position = position_dodge2(
  width = 1,
  preserve = "total",
  padding = 0.1,
  reverse = FALSE

))+
  theme(axis.text.x = element_text(size = 8, angle = 45, hjust = 1), panel.spacing.x = unit(0.001, "cm"),
        strip.text.x = element_blank()) +
scale_color_d3("category20") +
  xlab("AUROC") +
  ylab("Feautre Set") +
  ggtitle("") # Agnostic Model: XGBoost: County - AHRQ Individual Domains

plt_by_feats # Show plot


########
```

# Experiment 7:[TRACT] AHRQ 5 domains vs. total AHRQ
```{r}
# First filter for these subgroups only
sgs_selected <- c("black", "white") # c("black", "white", "male", "female", "other")
subset_sgs <- filter(df_2_baseline_sg_results, subgroup %in%  sgs_selected)
# Stratify by feat, then by subgroup.
by_feat_groups <- subset_sgs %>% group_by(feat, subgroup) %>% summarise(mean_auc = auc) %>% arrange(feat, desc(mean_auc))



feat_order <- c( "age_current",
        "sex",
        "demo",
        "hf_vars",
        "comorb",
        "hf_with_comorb",
        "demo_comorb",
        "charlson",
        "hf_with_charlson",

        "adi_national", "adi_state", 
        "sdi", "sdi_score", 
        "svi",
        
        "tot_tract_AHRQ_median",
        
        "tract_medianIMP_ahrq_1_socialcontext",
            "tract_medianIMP_ahrq_2_economiccontext",
            "tract_medianIMP_ahrq_3_education",
            "tract_medianIMP_ahrq_4_physicalinfrastructure",
            "tract_medianIMP_ahrq_5_healthcarecontext"


        )

by_feat_groups <- by_feat_groups[by_feat_groups$feat %in% feat_order, ]

by_feat_groups$feat <- factor(by_feat_groups$feat, levels=feat_order)

  

# Make plot
plt_by_feats <- ggplot(
    data = by_feat_groups, 
    aes(x=mean_auc, y=feat, group=feat, color=subgroup, group=INDEX, color=INDEX)) +
geom_line() +
  geom_point( position = position_dodge2(
  width = 1,
  preserve = "total",
  padding = 0.1,
  reverse = FALSE

))+
    
  theme(axis.text.x = element_text(size = 8, angle = 45, hjust = 1), panel.spacing.x = unit(0.001, "cm"),
        strip.text.x = element_blank()) +
scale_color_d3("category20") +
  ggtitle("Agnostic Model: Tract - AHRQ Individual Domains")

plt_by_feats # Show plot
```


# To answer question: "DOES RAW AQI/AHRQ DATA, OR COMBINING AQI/AHRQ WITH DEMO/COMORB, IMPROVE AUC WITHIN A SUBGROUP?"

```{r}
# Stratify by subgroup, then by feat
by_sgs <- df_2_baseline_sg_results %>% group_by(subgroup, feat) %>% summarise(mean_auc = auc) %>% group_by(subgroup) %>% arrange(subgroup, desc(mean_auc))


# 1.) Show black table (in decr AUC)
black_decr_auc <- filter(by_sgs, subgroup == "black")
black_decr_auc

# 2.) Show white table (in decr AUC)
white_decr_auc <- filter(by_sgs, subgroup == "white")
white_decr_auc

# Make plot
plt_by_feats <- ggplot(
    data = by_feat_groups, 
    aes(x=subgroup, y=mean_auc, group=feat, color=feat)) +
geom_line()+
geom_jitter(aes(x=subgroup,
        y = mean_auc,
        color = feat),
    size=2,
    show.legend=TRUE,
    width = 0.1) +
  theme(axis.text.x = element_text(size = 8, angle = 45, hjust = 1))

plt_by_feats # Show plot


###################
# Rename to black_mean_auc, white_mean_auc
colnames(black_decr_auc)[colnames(black_decr_auc) == "mean_auc"] ="Black: Mean AUROC"
colnames(white_decr_auc)[colnames(white_decr_auc) == "mean_auc"] ="White: Mean AUROC"

# Drop both subgroup columns.
black_decr_auc <- subset(black_decr_auc, select = -c(subgroup))
white_decr_auc <- subset(white_decr_auc, select = -c(subgroup))


# Merge on feat.
races_by_feats <- merge(black_decr_auc, white_decr_auc, by.x="feat", by.y="feat")

# Sort by descending AUC for *black*, not white. 
races_by_feats <- races_by_feats[order(races_by_feats$"Black: Mean AUROC", decreasing = TRUE),]  

# Plot
#data = matrix(races_by_feats, ncol=3, byrow=TRUE)
 
# specify the column names and row names of matrix
colnames(races_by_feats) = c('Features', 'Black: Mean AUROC', 'White: Mean AUROC')

# assign to table
LT_table = as.data.table(races_by_feats)


j1 <- which.max(unlist(LT_table[,"Black: Mean AUROC"]))
j2 <- which.max(unlist(LT_table[,"White: Mean AUROC"]))
col <- seq_len(ncol(LT_table))
LT_table[j1,"Black: Mean AUROC"] <- LT_table[j1,"Black: Mean AUROC"] %>% cell_spec(bold = col == j1)
LT_table[j2,"White: Mean AUROC"] <- LT_table[j2,"White: Mean AUROC"] %>% cell_spec(bold = col == j2)

LT_table[j1,"Black: Mean AUROC"]


LT_table %>%
  kbl(caption="Total Features: AUROC by Race",
       format= "html",
   col.names = c("Features", "Black: Mean AUROC", "White: Mean AUROC"),
                  align="r",
                  digits = 5
   ) %>%
   kable_classic(full_width = F, html_font = "cambria")
```


# E2 New: replace vs. agument Air quality
```{r}
#################################

# First filter for these subgroups only
sgs_selected <- c("black", "white") # c("black", "white", "male", "female", "other")
subset_sgs <- filter(df_2_baseline_sg_results, subgroup %in%  sgs_selected)
# Stratify by feat, then by subgroup.
by_feat_groups <- subset_sgs %>% group_by(feat, subgroup) %>% summarise(mean_auc = auc) %>% arrange(feat, desc(mean_auc))

fcheck <- df_2_baseline_sg_results$feat


feat_order <- c( "age_current",
        "sex",
        "demo",
        "hf_vars",
        "comorb",
        "hf_with_comorb",
        "demo_comorb",
        "charlson",
        "hf_with_charlson",

        "adi_national", "adi_state", 
        "svi",
        "sdi",
        
        
        
        "county_AHRQ_median_without_EPAA",
        "tot_county_AHRQ_median_without_EPAA_w_EPA_AQS_median", 
        "tot_county_AHRQ_median",
        "tot_county_AHRQ_median_w_EPAA_w_EPA_AQS_median"

        )


by_feat_groups <- by_feat_groups[by_feat_groups$feat %in% feat_order, ]

by_feat_groups$feat <- factor(by_feat_groups$feat, levels=feat_order)


# RENAME: 
RENAME_cols <- c("Age",
                 "Sex",
                 "Demo",
                 "HF Type",
                 "Comorb",
                 "HF Type+Comorb",
                 "Demo+Comorb",
                 "CCI",
                 "HF Type+CCI",
                 "ADI: National Rank",
                 "ADI: State Rank",
                 "SVI",
                 "SDI",
                 
                 "Neither: AHRQ - AHRQ EPA",
                 "AHRQ",
                 "AHRQ - AHRQ EPA + EPA AQS",
                 "Both: AHRQ + EPA AQS"

                  )


# "Neither: AHRQ*",
 # "Only AHRQ* + AHRQ EPA",
 # "Only AHRQ* + EPA AQS",
 # "Both: AHRQ + AHRQ EPA + EPA AQS"
                 
                 
        # "county_AHRQ_median_without_EPAA",
        # "tot_county_AHRQ_median_without_EPAA_w_EPA_AQS_median", 
        # "tot_county_AHRQ_median",
        # "tot_county_AHRQ_median_w_EPAA_w_EPA_AQS_median"




rename_map <- setNames(RENAME_cols, feat_order)
by_feat_groups <- by_feat_groups %>% mutate(feat = rename_map[as.character(feat)])


# Reorder again
by_feat_groups <- by_feat_groups[by_feat_groups$feat %in% RENAME_cols, ]
by_feat_groups$feat <- factor(by_feat_groups$feat, levels=rev(RENAME_cols))

  

# Make plot
plt_by_feats <- ggplot(
    data = by_feat_groups, 
    aes(x=mean_auc, y=feat, group=feat, color=subgroup, group=INDEX, color=INDEX)) +
geom_line() +
  geom_point( position = position_dodge2(
  width = 1,
  preserve = "total",
  padding = 0.1,
  reverse = FALSE

))+
  theme(axis.text.x = element_text(size = 8, angle = 45, hjust = 1), panel.spacing.x = unit(0.001, "cm"),
        strip.text.x = element_blank()) +
scale_color_d3("category20") + xlab("AUROC") + ylab("Feature Sets")
  ggtitle("") # Agnostic Model: XGBoost - AHRQ + Air Quality

plt_by_feats # Show plot
```


# Same e2, but using spatial imp (except AHRQ row uses median imp for EPAA)
```{r}



# First filter for these subgroups only
sgs_selected <- c("black", "white") # c("black", "white", "male", "female", "other")
subset_sgs <- filter(df_2_baseline_sg_results, subgroup %in%  sgs_selected)
# Stratify by feat, then by subgroup.
by_feat_groups <- subset_sgs %>% group_by(feat, subgroup) %>% summarise(mean_auc = auc) %>% arrange(feat, desc(mean_auc))

fcheck <- df_2_baseline_sg_results$feat


feat_order <- c( "age_current",
        "sex",
        "demo",
        "hf_vars",
        "comorb",
        "hf_with_comorb",
        "demo_comorb",
        "charlson",
        "hf_with_charlson",

        "adi_national", "adi_state", 
        "svi",
        "sdi",
        
        
        
        "county_AHRQ_median_without_EPAA",
        "tot_county_AHRQ_median_without_EPAA_w_EPA_AQS_spatial", 
        "tot_county_AHRQ_median",
        "tot_county_AHRQ_median_w_EPAA_spatial_w_EPA_AQS_spatial"


        )


by_feat_groups <- by_feat_groups[by_feat_groups$feat %in% feat_order, ]

by_feat_groups$feat <- factor(by_feat_groups$feat, levels=feat_order)


# RENAME: 
RENAME_cols <- c("Age",
                 "Sex",
                 "Demo",
                 "HF Type",
                 "Comorb",
                 "HF Type+Comorb",
                 "Demo+Comorb",
                 "CCI",
                 "HF Type+CCI",
                 "ADI: National Rank",
                 "ADI: State Rank",
                 "SVI",
                 "SDI",
                 
                 "Neither: AHRQ - AHRQ EPA",
                 "AHRQ",
                 "AHRQ - AHRQ EPA + EPA AQS",
                 "Both: AHRQ + EPA AQS"

                  )


# "Neither: AHRQ*",
 # "Only AHRQ* + AHRQ EPA",
 # "Only AHRQ* + EPA AQS",
 # "Both: AHRQ + AHRQ EPA + EPA AQS"
                 
                 
        # "county_AHRQ_median_without_EPAA",
        # "tot_county_AHRQ_median_without_EPAA_w_EPA_AQS_median", 
        # "tot_county_AHRQ_median",
        # "tot_county_AHRQ_median_w_EPAA_w_EPA_AQS_median"




rename_map <- setNames(RENAME_cols, feat_order)
by_feat_groups <- by_feat_groups %>% mutate(feat = rename_map[as.character(feat)])


# Reorder again
by_feat_groups <- by_feat_groups[by_feat_groups$feat %in% RENAME_cols, ]
by_feat_groups$feat <- factor(by_feat_groups$feat, levels=rev(RENAME_cols))

  

# Make plot
plt_by_feats <- ggplot(
    data = by_feat_groups, 
    aes(x=mean_auc, y=feat, group=feat, color=subgroup, group=INDEX, color=INDEX)) +
geom_line() +
  geom_point( position = position_dodge2(
  width = 1,
  preserve = "total",
  padding = 0.1,
  reverse = FALSE

))+
  theme(axis.text.x = element_text(size = 8, angle = 45, hjust = 1), panel.spacing.x = unit(0.001, "cm"),
        strip.text.x = element_blank()) +
scale_color_d3("category20") + xlab("AUROC") + ylab("Feature Sets")
  ggtitle("") # Agnostic Model: XGBoost - AHRQ + Air Quality

plt_by_feats # Show plot
```


