---
title: "generate_subgroup_statistics"
output: html_document
date: "2023-08-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(tidyr)
#library(tidyverse)
library(ggplot2)
library(gridExtra)
library(dplyr)
#install.packages("kableExtra")
library(kableExtra)
library(reshape2)
# Corr plots
library(ggcorrplot) 
library(corrplot)
library(pBrackets)


# Includes AHRQ data. 

df_clean_baseline_year <- read.csv("./__ input features CSV file here __")
```

# Race statistics: figure
## Columns for use: 
white <int>
black <int>
other <int> ( I assume this is race )

```{r}
library(reshape2)
race_df = subset(df_clean_baseline_year, select = c(white, black, other)) 
race_df$id <- 1:nrow(race_df)

race_cat <- race_df %>%
  group_by(id) %>%
  mutate_each(funs( as.numeric(as.character(.)))) %>%
  tidyr::gather(race, val, -id) %>%
  filter(val == 1) %>%
  select(-val) %>%
  arrange(id)

# Race ggplot: raw counts
race_bar_raw <- race_cat %>% 
  ggplot(aes(x = race)) +
  geom_bar() +
  labs(y = "Frequency", x = "Race")
race_bar_raw

# Race ggplot: proportions
race_bar_prop <- race_cat %>% 
  ggplot(aes(x = race, y = after_stat(count)/sum(after_stat(count)))) +
  geom_bar() +
  labs(y = "Proportion", x= "Race")
race_bar_prop

# No nas
# sum(is.na(race_df))
```


# Sex (or binary gender) statistics: figure
female <int>
... male: nrow - number of females

```{r}
sex_df = subset(df_clean_baseline_year, select = c(female)) 
sex_df$id <- 1:nrow(sex_df)

sex_df$sex <- with(sex_df, ifelse(female == 0, 'male', 'female'))

# Sex ggplot: raw counts
sex_bar_raw <- sex_df %>% 
  ggplot(aes(x = sex)) +
  geom_bar() +
  labs(y = "Frequency", x = "Sex")
sex_bar_raw
# Sex ggplot: proportions
sex_bar_prop <- sex_df %>% 
  ggplot(aes(x = sex, y = after_stat(count)/sum(after_stat(count)))) +
  geom_bar() +
  labs(y = "Proportion", x= "Sex")
sex_bar_prop
# No nas
# sum(is.na(sex_df))

# Counts: 
cat("Number of females: ",  as.character(sum(sex_df$sex == 'female')), "\n")
cat("Number of males: ",   as.character(sum(sex_df$sex == 'male')), "\n")

# Proportions:
cat("Number of females: ",  as.character(sum(sex_df$sex == 'female')/nrow(sex_df)), "\n")
cat("Number of males: ",   as.character(sum(sex_df$sex == 'male')/nrow(sex_df)))







```

# 6 subgroup combinations: 
## c(white_male, black_male, other_male, white_female, black_female, other_female)

```{r}
# New column: 'subgroup': c(white_male, black_male, other_male, white_female, black_female, other_female)
subgroup_df = subset(df_clean_baseline_year, select = c(female, white, black, other)) 
head(subgroup_df)

subgroup_df$subgroup <- with(subgroup_df, 
      ifelse(female == 0, 
        ifelse(white == 1, 'white_male', 
          ifelse(black == 1, 'black_male', 'other_male' )), 
            ifelse(white == 1, 'white_female', 
              ifelse(black == 1, 'black_female', 'other_female')) ))

# Use column 'subgroup' for bar plot:

# Subgroup ggplot: raw county
subgroup_bar_raw <- subgroup_df %>% 
  ggplot(aes(x = subgroup)) +
  geom_bar() +
  labs(y = "Frequency", x = "Subgroup") + 
  theme(axis.text.x = element_text(size = 6))
subgroup_bar_raw


# Subgroup ggplot: proportions
subgroup_bar_prop <- subgroup_df %>% 
  ggplot(aes(x = subgroup, y = after_stat(count)/sum(after_stat(count)))) +
  geom_bar() +
  labs(y = "Proportion", x= "Subgroup") +
  theme(axis.text.x = element_text(size = 6))
subgroup_bar_prop
```

# Medicare or Medicade, or private insurance
Medicare <int>
Medicaid <int>
privinsurance <int>


```{r}
insurace_df = subset(df_clean_baseline_year, select = c(Medicare, Medicaid, privinsurance)) 
insurace_df$id <- 1:nrow(insurace_df)

ins_cat <- insurace_df %>%
  group_by(id) %>%
  mutate_each(funs( as.numeric(as.character(.)))) %>%
  tidyr::gather(insurance_type, val, -id) %>%
  filter(val == 1) %>%
  select(-val) %>%
  arrange(id)

# Insurance ggplot: raw counts
ins_bar_raw <- ins_cat %>% 
  ggplot(aes(x = insurance_type)) +
  geom_bar() +
  labs(y = "Frequency", x = "Insurance")
ins_bar_raw

# Insurance ggplot: proportions
ins_bar_prop <- ins_cat %>% 
  ggplot(aes(x = insurance_type, y = after_stat(count)/sum(after_stat(count)))) +
  geom_bar() +
  labs(y = "Proportion", x= "Insurance")
ins_bar_prop

# Assert No nas
# sum(is.na(insurace_df))
```


```{r}
#################
# Combined figure, for proportions
#################

grid.arrange(race_bar_prop, sex_bar_prop, subgroup_bar_prop, ins_bar_prop,
             top = "Dataset Demographics", bottom = "", 
             left = "", right = "",
             widths = c(6, 4), heights = c(2, 2))

# Create a custom theme to set a common y-axis label
common_y_label_theme <- theme(axis.title.y = element_text(vjust = 0.5, angle = 0))


#################
# Same figure, for raw counts
#################

grid.arrange(race_bar_raw, sex_bar_raw, subgroup_bar_raw, ins_bar_raw,
             top = "Dataset Demographics", bottom = "", 
             left = "", right = "",
             widths = c(6, 4), heights = c(2, 2))

# Create a custom theme to set a common y-axis label
common_y_label_theme <- theme(axis.title.y = element_text(vjust = 0.5, angle = 0))
```


# Entire dataset: age quartiles

```{r}
age_df = subset(df_clean_baseline_year, select = c(age_current)) 
age_df$id <- 1:nrow(age_df)

# First (entire dataset), find quartiles of age_current column
quarts <- quantile(age_df$age_current, probs = c(0,0.25,0.5,0.75,1))

# Also, Exclude patients with 'age_current' > 85
# sum(age_df$age_current > 105) # TODO: ^^ check on this??
# Drop row if age_current > 85
age_df <- age_df[age_df$age_current <= 85,] # from 31020 to 25314 patients.


# Second, plot histogram. Change bin size?
hist(age_df$age_current,
     xlab = "Age at Admission",
     main = "Age Frequency Distribution"
)

# (entire dataset) Third, plot quartiles bins.


# Race: Do age within subgroups: 
# HISTOGRAM FOR AGE by RACE:
race_age_df = subset(df_clean_baseline_year, select = c(age_current, black, white, other)) 
race_age_df$id <- 1:nrow(race_age_df)
race_age_df <- race_age_df[race_age_df$age_current <= 85,]
race_age_df$race <- with(race_age_df, ifelse(black == 1, "black", ifelse(white == 1, "white", "other")))
# Then select ONLY c(id, age_current, race)
race_age_df <- subset(race_age_df, select = c(id, age_current, race)) 


# Plot
# Bins = 30: more smooth.
ggplot(race_age_df, aes(x = age_current, fill = race, color = race)) + 
  geom_histogram(alpha = 0.5,
                 position = "dodge", bins = 10) + 
  xlab("Age at Admission") + 
  ylab("Count")
  ggtitle("Age Frequency Distribution")

##########################
# Sex: Do age within subgroups: 
# HISTOGRAM FOR AGE by Sex:
sex_age_df = subset(df_clean_baseline_year, select = c(age_current, female)) 
sex_age_df$id <- 1:nrow(sex_age_df)
sex_age_df <- sex_age_df[sex_age_df$age_current <= 85,]
sex_age_df$sex <- with(sex_age_df, ifelse(female == 1, "female", "male"))
# Then select ONLY c(id, age_current, sex)
sex_age_df <- subset(sex_age_df, select = c(id, age_current, sex)) 


# Plot
# Bins = 30: more smooth.
ggplot(sex_age_df, aes(x = age_current, fill = sex, color = sex)) + 
  geom_histogram(alpha = 0.5, bins = 20) + 
  xlab("Age at Admission") + 
  ylab("Count")
  ggtitle("Age Frequency Distribution")


  
  ###########################
sg_age_df = subset(df_clean_baseline_year, select = c(age_current, female, white, black, other)) 
sg_age_df$id <- 1:nrow(sg_age_df)
sg_age_df <- sg_age_df[sg_age_df$age_current <= 85,]


sg_age_df$subgroup <- with(sg_age_df, 
      ifelse(female == 0, 
        ifelse(white == 1, 'white_male', 
          ifelse(black == 1, 'black_male', 'other_male' )), 
            ifelse(white == 1, 'white_female', 
              ifelse(black == 1, 'black_female', 'other_female')) ))

# Then select ONLY c(id, age_current, race)
sg_age_df <- subset(sg_age_df, select = c(id, age_current, subgroup)) 


# Plot
# Bins = 30: more smooth.
ggplot(sg_age_df, aes(x = age_current, fill = subgroup, color = subgroup)) + 
  geom_histogram(alpha = 0.5,
                 position = "dodge", bins = 10) + 
  xlab("Age at Admission") + 
  ylab("Count")
  ggtitle("Age Frequency Distribution")
```

# AGE by quartiles: 

```{r}
race_age_df = subset(df_clean_baseline_year, select = c(age_current, black, white, other)) 
race_age_df$id <- 1:nrow(race_age_df)
race_age_df <- race_age_df[race_age_df$age_current <= 85,]
race_age_df$race <- with(race_age_df, ifelse(black == 1, "black", ifelse(white == 1, "white", "other")))
# Then select ONLY c(id, age_current, race)
race_age_df <- subset(race_age_df, select = c(id, age_current, race)) 

# Stratify by quartiles within each race:
race_age_df <- race_age_df %>%
  group_by(race) %>%
  mutate(q1 = quantile(age_current, 0.25),
         q2 = quantile(age_current, 0.5),
         q3 = quantile(age_current, 0.75))

# Create the 'quartile' column based on quartile values
race_age_df <- race_age_df %>%
  mutate(quartile = case_when(
    age_current < q1 ~ 1,
    age_current >= q1 & age_current < q2 ~ 2,
    age_current >= q2 & age_current < q3 ~ 3,
    age_current >= q3 ~ 4,
    TRUE ~ NA_real_  # Handle cases not covered
  )) %>%
  select(-q1, -q2, -q3)  # Remove quartile calculation columns if needed

race_age_df

# Plot
# Bins = 30: more smooth.
ggplot(race_age_df, aes(x = age_current, fill = race, color = race)) + 
  geom_histogram(alpha = 0.5,
                 position = "dodge", bins = 10) + 
  xlab("Age at Admission") + 
  ylab("Count")
  ggtitle("Age Frequency Distribution")
  


```






# Readmission rates: 
- overall
- by subgroup: 

# READMIT RATES PLOTS (by race):
```{r}

readmit_by_race <- subset(df_clean_baseline_year, select = c(white, black, other, readmit30bin)) 

white_readmit_rate <- nrow(filter(readmit_by_race, white == 1 & readmit30bin == 1)) / nrow(filter(readmit_by_race, white == 1))
black_readmit_rate <- nrow(filter(readmit_by_race, black == 1 & readmit30bin == 1)) / nrow(filter(readmit_by_race, black == 1))
other_readmit_rate <- nrow(filter(readmit_by_race, other == 1 & readmit30bin == 1)) / nrow(filter(readmit_by_race, other == 1))


white_readmit_rate
black_readmit_rate
other_readmit_rate

# Plot
data = matrix(c(white_readmit_rate, black_readmit_rate, other_readmit_rate), ncol=3, byrow=TRUE)
 
# specify the column names and row names of matrix
colnames(data) = c('White','Black','Other')

# assign to table
LT_table =as.data.table(data)

LT_table %>%
  kbl(caption="30 Day Readmission Rate by Race",
       format= "html",
   col.names = c("White", "Black", "Other"),
                  align="r",
                  digits = 3
   ) %>%
   kable_classic(full_width = F, html_font = "cambria")
```


# READMIT RATES (by sex): 
```{r}
# READMIT RATES (by sex): 

readmit_by_sex <- subset(df_clean_baseline_year, select = c(female, readmit30bin)) 

male_readmit_rate <- nrow(filter(readmit_by_sex, female == 0 & readmit30bin == 1)) / nrow(filter(readmit_by_sex, female == 0))
female_readmit_rate <- nrow(filter(readmit_by_sex, female == 1 & readmit30bin == 1)) / nrow(filter(readmit_by_sex, female == 1))

male_readmit_rate
female_readmit_rate


# Plot
data = matrix(c(male_readmit_rate, female_readmit_rate), ncol=2, byrow=TRUE)
 
# specify the column names and row names of matrix
colnames(data) = c('Male','Female')

# assign to table
LT_table =as.data.table(data)

# LT_table %>%
#   kbl(caption="30 Day Readmission Rate by Sex",
#        format= "html",
#    col.names = c("Male", "Female"),
#                   align="r",
#                   digits = 3
#    ) %>%
#    kable_classic(full_width = F, html_font = "cambria")

LT_table %>%
  kbl(caption="30-d HF Readmission Rate by Sex",
       format= "latex", 
   col.names = c("Male", "Female"),
                  align="r",
                  digits = 3
   ) %>%
   kable_classic(full_width = FALSE, latex_options = "scale_down")





```


# READMIT RATES: by subgroup (white_male, black_male, other_male, white_female, black_female, other_female)
```{r}
#################
# READMIT RATES: by subgroup (white_male, black_male, other_male, white_female, black_female, other_female)
subgroup_df = subset(df_clean_baseline_year, select = c(female, white, black, other, readmit30bin)) 

subgroup_df$subgroup <- with(subgroup_df, 
      ifelse(female == 0, 
        ifelse(white == 1, 'white_male', 
          ifelse(black == 1, 'black_male', 'other_male' )), 
            ifelse(white == 1, 'white_female', 
              ifelse(black == 1, 'black_female', 'other_female')) ))

readmit_by_sg <- subset(subgroup_df, select = c(subgroup, readmit30bin)) 

whitemale_readmit_rate <- nrow(filter(readmit_by_sg, subgroup == "white_male" & readmit30bin == 1)) / nrow(filter(readmit_by_sg, subgroup == "white_male"))

whitefemale_readmit_rate <- nrow(filter(readmit_by_sg, subgroup == "white_female" & readmit30bin == 1)) / nrow(filter(readmit_by_sg, subgroup == "white_female"))

blackmale_readmit_rate <- nrow(filter(readmit_by_sg, subgroup == "black_male" & readmit30bin == 1)) / nrow(filter(readmit_by_sg, subgroup == "black_male"))

blackfemale_readmit_rate <- nrow(filter(readmit_by_sg, subgroup == "black_female" & readmit30bin == 1)) / nrow(filter(readmit_by_sg, subgroup == "black_female"))

othermale_readmit_rate <- nrow(filter(readmit_by_sg, subgroup == "other_male" & readmit30bin == 1)) / nrow(filter(readmit_by_sg, subgroup == "other_male"))

otherfemale_readmit_rate <- nrow(filter(readmit_by_sg, subgroup == "other_female" & readmit30bin == 1)) / nrow(filter(readmit_by_sg, subgroup == "other_female"))

whitemale_readmit_rate
blackmale_readmit_rate
othermale_readmit_rate


whitefemale_readmit_rate
blackfemale_readmit_rate
otherfemale_readmit_rate


# Plot
data = matrix(c(whitemale_readmit_rate, 
                blackmale_readmit_rate, 
                othermale_readmit_rate, 
                whitefemale_readmit_rate,
                blackfemale_readmit_rate,
                otherfemale_readmit_rate
                ), ncol=6, byrow=TRUE)
 
# specify the column names and row names of matrix
colnames(data) = c('White Male','Black Male','Other Male', 'White Female', 'Black Female', 'Other Female')

# assign to table
LT_table =as.data.table(data)


LT_table %>%
  kbl(caption = "30-d HF Readmission Rate by Race and Sex",
      format = "latex", # Change format to LaTeX
      col.names = c("White Male", "Black Male", "Other Male", "White Female", "Black Female", "Other Female"),
      align = "r",
      digits = 3
  ) %>%
  kable_classic(full_width = FALSE, latex_options = "scale_down") # Use latex_options to customize LaTeX output
```


# Total readmission table: 

```{r}

#################
# READMIT RATES: by subgroup (white_male, black_male, other_male, white_female, black_female, other_female)

####
readmit_by_race <- subset(df_clean_baseline_year, select = c(white, black, other, readmit30bin)) 

white_readmit_rate <- nrow(filter(readmit_by_race, white == 1 & readmit30bin == 1)) / nrow(filter(readmit_by_race, white == 1))
black_readmit_rate <- nrow(filter(readmit_by_race, black == 1 & readmit30bin == 1)) / nrow(filter(readmit_by_race, black == 1))
other_readmit_rate <- nrow(filter(readmit_by_race, other == 1 & readmit30bin == 1)) / nrow(filter(readmit_by_race, other == 1))


####
readmit_by_sex <- subset(df_clean_baseline_year, select = c(female, readmit30bin)) 

male_readmit_rate <- nrow(filter(readmit_by_sex, female == 0 & readmit30bin == 1)) / nrow(filter(readmit_by_sex, female == 0))
female_readmit_rate <- nrow(filter(readmit_by_sex, female == 1 & readmit30bin == 1)) / nrow(filter(readmit_by_sex, female == 1))

####
subgroup_df = subset(df_clean_baseline_year, select = c(female, white, black, other, readmit30bin)) 

subgroup_df$subgroup <- with(subgroup_df, 
      ifelse(female == 0, 
        ifelse(white == 1, 'white_male', 
          ifelse(black == 1, 'black_male', 'other_male' )), 
            ifelse(white == 1, 'white_female', 
              ifelse(black == 1, 'black_female', 'other_female')) ))

readmit_by_sg <- subset(subgroup_df, select = c(subgroup, readmit30bin)) 

whitemale_readmit_rate <- nrow(filter(readmit_by_sg, subgroup == "white_male" & readmit30bin == 1)) / nrow(filter(readmit_by_sg, subgroup == "white_male"))

whitefemale_readmit_rate <- nrow(filter(readmit_by_sg, subgroup == "white_female" & readmit30bin == 1)) / nrow(filter(readmit_by_sg, subgroup == "white_female"))

blackmale_readmit_rate <- nrow(filter(readmit_by_sg, subgroup == "black_male" & readmit30bin == 1)) / nrow(filter(readmit_by_sg, subgroup == "black_male"))

blackfemale_readmit_rate <- nrow(filter(readmit_by_sg, subgroup == "black_female" & readmit30bin == 1)) / nrow(filter(readmit_by_sg, subgroup == "black_female"))

othermale_readmit_rate <- nrow(filter(readmit_by_sg, subgroup == "other_male" & readmit30bin == 1)) / nrow(filter(readmit_by_sg, subgroup == "other_male"))

otherfemale_readmit_rate <- nrow(filter(readmit_by_sg, subgroup == "other_female" & readmit30bin == 1)) / nrow(filter(readmit_by_sg, subgroup == "other_female"))

whitemale_readmit_rate
blackmale_readmit_rate
othermale_readmit_rate


whitefemale_readmit_rate
blackfemale_readmit_rate
otherfemale_readmit_rate


# Plot
data = matrix(c(white_readmit_rate,
                black_readmit_rate,
                male_readmit_rate,
                female_readmit_rate,
                
                whitemale_readmit_rate, 
                blackmale_readmit_rate,
                whitefemale_readmit_rate,
                blackfemale_readmit_rate
                ), ncol=8, byrow=TRUE)
 
# specify the column names and row names of matrix
colnames(data) = c('White', 'Black', 'Male', 'Female', 'White Male','Black Male', 'White Female', 'Black Female')

# assign to table
LT_table =as.data.table(data)

LT_table %>%
  kbl(caption = "30-d HF Readmission Rate by Race and Sex",
      format = "latex", # Change format to LaTeX
      col.names = c("White", "Black", "Male", "Female", "White Male", "Black Male", "White Female", "Black Female"),
      align = "c",
      digits = 3
  ) %>%
  kable_classic(full_width = FALSE, latex_options = "scale_down") # Use latex_options to customize LaTeX output


```

# Build Correlation matrix: 
- See Fig 1A.
# ggplot2 correlation matrix: http://www.sthda.com/english/wiki/ggplot2-quick-correlation-matrix-heatmap-r-software-and-data-visualization

```{r}
# X-axis: Basic demogrphic information
# Black
# Male
# Age: 18-55
# Age: 55-65
# Age: 65-75
# Age: 75+
# Medicaid
# Medicare



# Only display MOST correlated features (by abs val) with race = "Black".





corr_input_df <- df_clean_baseline_year
corr_input_df$age_18_55 <- with(df_clean_baseline_year, ifelse((age_current >= 18 & age_current < 55), 1, 0))
corr_input_df$age_55_65 <- with(df_clean_baseline_year, ifelse((age_current >= 55 & age_current < 65), 1, 0))
corr_input_df$age_65_75 <- with(df_clean_baseline_year, ifelse((age_current >= 65 & age_current < 75), 1, 0))
corr_input_df$age_75_up <- with(df_clean_baseline_year, ifelse(age_current >= 75, 1, 0))


demo_cols_keep <- c("black",
                     "male",
                     "age_18_55",
                     "age_55_65",
                     "age_65_75",
                     "age_75_up",
                     "Medicaid")


# NOTE: We use county & median feature imp here for all correlation measures. 
### AHRQ SDOHD CATEGORIES
#   - Median Household Income: Median household income (dollars, inflation-adjusted to data file year)
#   - % Receiving Food Stamps: Percentage of households that received food stamps/SNAP, past 12 months
#   - % Commuting via Public Transit: Percentage of workers taking public transportation, excluding taxicab (ages 16 and over)
#   - % Less than High School Educ: Percentage of population with less than high school education (ages 25 and over)
#   - % Non-citizens: Percentage of population who are not U.S. citizens
#   - Distance from Clinic: Median distance in miles to the nearest urgent care, calculated using population weighted tract centroids in the county
ahrq_cols_keep <- c("county_medianIMP_ACS_MEDIAN_HH_INC", 
                    "county_medianIMP_ACS_PCT_HH_FOOD_STMP",
                    "county_medianIMP_ACS_PCT_PUBL_TRANSIT",
                    "county_medianIMP_ACS_PCT_LT_HS",
                    "county_medianIMP_ACS_PCT_NON_CITIZEN",
                    "county_medianIMP_HIFLD_MEDIAN_DIST_UC")



### ADI categories: 

adi_cols_keep <- c("ADI_national_rank",
                  "ADI_state_rank")


### SVI categories: 
#Socioeconomic, 
#Household Composition & Disability, 
#Minority Status & Language, 
#Housing Type & Transportation.
svi_cols_keep <- c("RPL_THEME1",
                  "RPL_THEME2",
                  "RPL_THEME3",
                  "RPL_THEME4")



### SDI categories: 

sdi_cols_keep <- c("sdi",
                  "percnt_ltfpl100",
                  "percnt_singlparntfly",
                  "percnt_dropout",
                  "percnt_hhnocar",
                  "percnt_rentoccup",
                  "percnt_crowding",
                  "percnt_nonemp")




# Subset to get only demo_cols_keep, ahrq_cols_keep, and svi_cols_keep
corr_input_df <- corr_input_df[, c(demo_cols_keep, ahrq_cols_keep, adi_cols_keep, svi_cols_keep, sdi_cols_keep)]


# Rename columns:
RENAME_demo_cols_keep <- c("Black",
                     "Male",
                     "Age: 18-55",
                     "Age: 55-65",
                     "Age: 65-75",
                     "Age: 75+",
                     "Medicaid")

RENAME_ahrq_cols_keep <- c("Median Household Income", 
                    "% Receiving Food Stamps",
                    "% Commuting via Public Transit",
                    "% Less Than High School Educ",
                    "% Non-citizens",
                    "Median Distance From Clinic")
RENAME_adi_cols_keep <- c("ADI: National Rank",
                  "ADI: State Rank")


RENAME_svi_cols_keep <- c("Socioeconomic Status",
                  "Household Composition & Disability",
                  "Minority Status & Language",
                  "Housing Type & Transportation")

RENAME_sdi_cols_keep <- c("SDI",
                  "% With <100% Federal Poverty Level",
                  "% Single-parent Households",
                  "% With Less Than 12 Years Educ",
                  "% With No Car",
                  "% Living in Renter-occupied Housing Units",
                  "% Living in Crowded Housing Units",
                  "% Non-employed")


for(i in 1:length(demo_cols_keep)){
  colnames(corr_input_df)[colnames(corr_input_df) == demo_cols_keep[i]] = RENAME_demo_cols_keep[i]
}
for(i in 1:length(ahrq_cols_keep)){
  colnames(corr_input_df)[colnames(corr_input_df) == ahrq_cols_keep[i]] = RENAME_ahrq_cols_keep[i]
}
for(i in 1:length(adi_cols_keep)){
  colnames(corr_input_df)[colnames(corr_input_df) == adi_cols_keep[i]] = RENAME_adi_cols_keep[i]
}
for(i in 1:length(svi_cols_keep)){
  colnames(corr_input_df)[colnames(corr_input_df) == svi_cols_keep[i]] = RENAME_svi_cols_keep[i]
}
for(i in 1:length(sdi_cols_keep)){
  colnames(corr_input_df)[colnames(corr_input_df) == sdi_cols_keep[i]] = RENAME_sdi_cols_keep[i]
}



# Calculate correlation matrix
cormat <- round(cor(corr_input_df), 3)

## Now reshape the data  (same as before)
# Subset columns from 'demo_cols_keep'.
cormat = cormat[, RENAME_demo_cols_keep]

# Subset rows that are NOT in 'demo_cols_keep'
cormat = cormat[c(RENAME_ahrq_cols_keep, RENAME_adi_cols_keep, RENAME_svi_cols_keep, RENAME_sdi_cols_keep), ]



# Save plot as PNG.
png(file="../figures/sdohs_corr.png", res=500, width=5000, height=5000)


# SHOW CORR HEATMAP
# Color options: https://cran.r-project.org/web/packages/corrplot/vignettes/corrplot-intro.html
corrplot(as.matrix(cormat), tl.col = 'black', cl.ratio = 0.3, is.corr=TRUE, tl.srt=45, col = COL2('RdBu', 10)) # Set is.corr TRUE since we're passing in the cor matrix.

mtext(text = c("(5) SDI", "(4) SVI", "(3) ADI"), side = 2, line = -2, at = c(8, 12, 14), las = 1, font = 2)
mtext(text = c("(1) AHRQ"), side = 2, line = -3, at = c(20), las = 1, font = 2)


dev.off()

#ggcorrplot(cormat, hc.order = TRUE, type = "lower", outline.col = "white", 
#           ggtheme = ggplot2::theme_gray,
#           colors = c("#6D9EC1", "white", "#E46726"))
```


# Air quality features correlation w/ demo feats: AHRQ AQI
```{r,fig.width=6, fig.height=4}
#- AHRQ EPAA (check all 3 imp methods)
#- EPA AQS (check all 3 imp methods)

# X-axis: Basic demogrphic information
# Black
# Male
# Age: 18-55
# Age: 55-65
# Age: 65-75
# Age: 75+
# Medicaid
# Medicare



# Only display MOST correlated features (by abs val) with race = "Black".





corr_input_df <- df_clean_baseline_year
corr_input_df$age_18_55 <- with(df_clean_baseline_year, ifelse((age_current >= 18 & age_current < 55), 1, 0))
corr_input_df$age_55_65 <- with(df_clean_baseline_year, ifelse((age_current >= 55 & age_current < 65), 1, 0))
corr_input_df$age_65_75 <- with(df_clean_baseline_year, ifelse((age_current >= 65 & age_current < 75), 1, 0))
corr_input_df$age_75_up <- with(df_clean_baseline_year, ifelse(age_current >= 75, 1, 0))


demo_cols_keep <- c("black",
                     "male",
                     "age_18_55",
                     "age_55_65",
                     "age_65_75",
                     "age_75_up",
                     "Medicaid")


# NOTE: We use county & median feature imp here for all correlation measures. 
### AHRQ SDOHD CATEGORIES
#   - Median Household Income: Median household income (dollars, inflation-adjusted to data file year)
#   - % Receiving Food Stamps: Percentage of households that received food stamps/SNAP, past 12 months
#   - % Commuting via Public Transit: Percentage of workers taking public transportation, excluding taxicab (ages 16 and over)
#   - % Less than High School Educ: Percentage of population with less than high school education (ages 25 and over)
#   - % Non-citizens: Percentage of population who are not U.S. citizens
#   - Distance from Clinic: Median distance in miles to the nearest urgent care, calculated using population weighted tract centroids in the county

AHRQ_EPAA_median_cols_keep <- c("county_medianIMP_EPAA_2NDMAX_CO_1HR","county_medianIMP_EPAA_2NDMAX_CO_8HR","county_medianIMP_EPAA_98PR_NO2_1HR","county_medianIMP_EPAA_MEAN_NO2_1HR","county_medianIMP_EPAA_2NDMAX_O3_1HR","county_medianIMP_EPAA_4THMAX_O3_8HR","county_medianIMP_EPAA_MAX_PB_3MON","county_medianIMP_EPAA_2NDMAX_PM10_24HR","county_medianIMP_EPAA_MEAN_WTD_PM10","county_medianIMP_EPAA_MEAN_WTD_PM25","county_medianIMP_EPAA_98PR_PM25_DAILY","county_medianIMP_EPAA_99PR_SO2_1HR","county_medianIMP_EPAA_2NDMAX_SO2_24HR","county_medianIMP_EPAA_MEAN_SO2_1HR")

EPA_AQS_median_cols_keep <- c("medianIMP.Days.with.AQI","medianIMP.Good.Days","medianIMP.Moderate.Days","medianIMP.Unhealthy.for.Sensitive.Groups.Days","medianIMP.Unhealthy.Days","medianIMP.Very.Unhealthy.Days","medianIMP.Hazardous.Days","medianIMP.Max.AQI","medianIMP.X90th.Percentile.AQI","medianIMP.Median.AQI","medianIMP.Days.CO","medianIMP.Days.NO2","medianIMP.Days.Ozone","medianIMP.Days.PM2.5","medianIMP.Days.PM10")


# Subset to get only demo_cols_keep, ahrq_cols_keep, and svi_cols_keep
corr_input_df <- corr_input_df[, c(demo_cols_keep, AHRQ_EPAA_median_cols_keep, EPA_AQS_median_cols_keep)]


# Rename columns:
RENAME_demo_cols_keep <- c("Black",
                     "Male",
                     "Age: 18-55",
                     "Age: 55-65",
                     "Age: 65-75",
                     "Age: 75+",
                     "Medicaid")

# county_medianIMP_EPAA_2NDMAX_CO_1HR: 2nd highest 1-hour measurement of Carbon Monoxide (CO) in the year (ppm)
# county_medianIMP_EPAA_2NDMAX_CO_8HR: 2nd highest non-overlapping 8-hour average of Carbon Monoxide (CO) in the year (ppm)
# county_medianIMP_EPAA_98PR_NO2_1HR: 98th percentile of the daily max 1-hour measurements of Nitrogen Dioxide (NO2) in the year (ppb)
# county_medianIMP_EPAA_MEAN_NO2_1HR: Annual mean of all the 1-hour measurements of Nitrogen Dioxide (NO2) in the year (ppb)
# county_medianIMP_EPAA_2NDMAX_O3_1HR: 2nd highest daily max 1-hour measurement of Ozone (O3) in the year (ppm)
# county_medianIMP_EPAA_4THMAX_O3_8HR: 4th highest daily max 8-hour average of Ozone (O3) in the year (ppm)
# county_medianIMP_EPAA_MAX_PB_3MON: Maximum of all rolling 3-month averages of Lead (Pb) in the year (ug/m3)
# county_medianIMP_EPAA_2NDMAX_PM10_24HR: 2nd highest 24-hour average of PM10 in the year
# county_medianIMP_EPAA_MEAN_WTD_PM10: Weighted annual mean (mean weighted by calendar quarter) for the year of PM10 (ug/m3)
# county_medianIMP_EPAA_MEAN_WTD_PM25: Weighted annual mean (mean weighted by calendar quarter) for the year of PM2.5 (ug/m3)
# county_medianIMP_EPAA_98PR_PM25_DAILY: 98th percentile of the daily average measurements in the year of PM2.5 (ug/m3)
# county_medianIMP_EPAA_99PR_SO2_1HR: 99th percentile of the daily max 1-hour measurements of Sulfur Dioxide (SO2) in the year
# county_medianIMP_EPAA_2NDMAX_SO2_24HR: 2nd highest 24-hour average of Sulfur Dioxide (SO2) in the year
# county_medianIMP_EPAA_MEAN_SO2_1HR: Annual mean of all the 1-hour measurements of Sulfur Dioxide (SO2) in the year (ppb)
rename_AHRQ_EPAA_median_cols_keep <- c("Year CO 2nd Highest 1-hr (ppm)",
                                       "Year CO 2nd Highest 8-hr (ppm)",
                                       "Year p98 NO2 Daily Max 1-hr (ppb)",
                                       "Year Mean 1-hr NO2 (ppb)",
                                       "2nd Highest 1-d Max O3",
                                       "4th Highest 1-d Max O3",
                                       "Max 3-mo Pb (ug/m3)",
                                       "2nd Highest 1-d Mean PM10",
                                       "Year Mean PM10 (ug/m3)",
                                       "Year Mean PM2.5 (ug/m3)",
                                       "Year p98 Daily Mean PM2.5 (ug/m3)",
                                       "Year p99 Daily Mean SO2",
                                       "Year 2nd Highest 1-d Mean SO2",
                                       "Year Mean 1-hr SO2 (ppb)")


# EPA AQS Variable descriptions here: https://www.epa.gov/outdoor-air-quality-data/about-air-data-reports
rename_EPA_AQS_median_cols_keep <- c("Days with AQI Measured",
                                     "Days Good AQI (<50)",
                                     "Days Moderate AQI (51-100)",
                                     "Days Unhealthy for Sensitive Groups (101-150)",
                                     "Days Unhealthy (151-200)",
                                     "Days Very Unhealthy (201-300)",
                                     "Days Hazardous (>300)",
                                     "Year Max Daily AQI",
                                     "p90 AQI",
                                     "Median AQI",
                                     "Days CO was Main Poll.",
                                     "Days NO2 was Main Poll.",
                                     "Days Ozone was Main Poll.",
                                     "Days PM2.5 was Main Poll.",
                                     "Days PM10 was Main Poll.")



for(i in 1:length(demo_cols_keep)){
  colnames(corr_input_df)[colnames(corr_input_df) == demo_cols_keep[i]] = RENAME_demo_cols_keep[i]
}
for(i in 1:length(AHRQ_EPAA_median_cols_keep)){
  colnames(corr_input_df)[colnames(corr_input_df) == AHRQ_EPAA_median_cols_keep[i]] = rename_AHRQ_EPAA_median_cols_keep[i]
}
for(i in 1:length(EPA_AQS_median_cols_keep)){
  colnames(corr_input_df)[colnames(corr_input_df) == EPA_AQS_median_cols_keep[i]] = rename_EPA_AQS_median_cols_keep[i]
}


# Calculate correlation matrix
cormat <- round(cor(corr_input_df), 3)

## Now reshape the data  (same as before)
# Subset columns from 'demo_cols_keep'.
cormat = cormat[, RENAME_demo_cols_keep]

# Subset rows that are NOT in 'demo_cols_keep'
cormat = cormat[c(rename_AHRQ_EPAA_median_cols_keep, rename_EPA_AQS_median_cols_keep), ]

# devtools::install_github("laresbernardo/lares")
# library(lares)
# 
# corr_cross(corr_input_df, # name of dataset
#   max_pvalue = 0.05, # display only significant correlations (at 5% level)
#   top = 10 # display top 10 couples of variables (by correlation coefficient)
# )

# SHOW CORR HEATMAP
# Color options: https://cran.r-project.org/web/packages/corrplot/vignettes/corrplot-intro.html
#pdf(file="../figures/AQ_corr.pdf")
png(file="../figures/AQ_corr.png", res=500, width=5000, height=5000)

corrplot(as.matrix(cormat), tl.col = 'black', cl.ratio = 0.4, is.corr=TRUE, tl.srt=45,
         tl.offset = 1, mar = c(2,5,2,2),
         col = COL2('RdBu', 10), addrect = 1 ) # Set is.corr TRUE since we're passing in the cor matrix.

mtext(text = c("EPA AQS", "SDOHD EPA"), side = 2, line = -2, at = c(14, 29), las = 1, font = 2)

# Specify the coordinates for the starting and ending points of the line
x_start <- -14  # Adjust this value to your desired x-position
y_start <- 15.5  # Adjust this value to your desired y-position
x_end <- -14  # Same x-position as the starting point
y_end <- 30  # Adjust this value to control the length of the line
# Blue bracket
#arrows(x_start, y_start, x_end, y_end, code = 3, angle = 90, length = 0.1, col = "blue")
# Black bracket
brackets(x1=x_start, y1=y_end, x2=x_end, y2=y_start, lwd=2, type=4, ticks=c(0, 0.5, 1))

# Specify the coordinates for the starting and ending points of the line
x_start <- -14  # Adjust this value to your desired x-position
y_start <- 1.5  # Adjust this value to your desired y-position
x_end <- -14  # Same x-position as the starting point
y_end <- 15  # Adjust this value to control the length of the line
# Blue bracket
#arrows(x_start, y_start, x_end, y_end, code = 3, angle = 90, length = 0.1, col = "blue")
# Black bracket
brackets(x1=x_start, y1=y_end, x2=x_end, y2=y_start, lwd=2, type=4, ticks=c(0, 0.5, 1))

dev.off()
```

# Dataset statistics (Table 1):
```{r}
# Note; we only show dimensions from the geographical levels used
svi_db <- c("SVI", "2014","Census Tract",  "15") # Years available: 2000, 2010, 2014, 2016, and 2018
sdi_db <- c("SDI","2015", "Census Tract", "7") # Years available: 2015
adi_db <- c("ADI", "2015", "Census Block Group", "17") # Years available: 2015, 2019

# Old 9-6 county intersection (2009-2020): 250 distinct features. 
# # SDOHD Years available: 2009-2020
# SDOHD:      (old 9-6 run did 2009+2020 intersection) County: d_2020=655, Tract: d_2020= 318 (excludes geo-ids)
ahrq_db <- c("SDOHD (AHRQ)", "2009-2020", "Census Tract | County | Intersection",  " 517 | 1307 | 485") 

EPA_db <- c("EPA AQS", "2009-2020", "County", "15") # Years available: 1980-2022



# Plot
data = matrix(c(ahrq_db, EPA_db, adi_db, svi_db, sdi_db), ncol=4, byrow=TRUE)
 


# specify the column names and row names of matrix
colnames(data) = c("SDOH Database", "Data Version/Year", "Geographic Levels Used", "d")

# assign to table
LT_table =as.data.table(data)


LT_table %>%
  kbl(caption="Characteristics of public datasets merged with patient HF data, where d is the number of distinct features.",
       format= "latex",  booktabs = T,
   col.names = c("SDOH Database", "Data Version/Year", "Geographic Levels Used", "d"),
                  align="c",
                  digits = 3
   ) %>%
   kable_classic(full_width = FALSE, latex_options = "scale_down")
```


# Feature sets plot
```{r}


all_EHR <- c("All EHR Data (Tabular)", "", "") 
EHR_1 <- c("", "-", "HF Classification") 
EHR_2 <- c("", "-", "Comorbidities") # Demo, comorb
EHR_3 <- c("", "-", "HF Classification+Comorbidities") 
EHR_4 <- c("", "-", "Charlson Comorbidity Index")
EHR_5 <- c("", "-", "HF Classification+Charlson Comorbidity Index") 



all_demo <- c("EHR Demographic Data", "", "")
demo_1 <- c("", "-", "Age") 
demo_2 <- c("", "-", "Sex") 
demo_3 <- c("", "-", "Age+Sex+Insurance Type+Race") 


all_SDOHD <- c("SDOHD", "", "") # Demo, comorb
SDOHD_1 <- c("All SDOHD (total)", "County", "Domains 1-5") # Demo, comorb
SDOHD_2 <- c("All SDOHD (total)", "Census Tract", "Domains 1-5") # Demo, comorb
SDOHD_3 <- c("All SDOHD (intersection)", "County", "Domains 1-5 intersection") # Demo, comorb
SDOHD_4 <- c("All SDOHD (intersection)", "Census Tract", "Domains 1-5 intersection") # Demo, comorb

all_EPA_AQS <- c("EPA AQS", "County", "EPA AQS Total") # Demo, comorb

all_ADI <- c("ADI", "", "") 
ADI_1 <- c("", "Census Block Group", "ADI National") 
ADI_2 <- c("", "Census Block Group", "ADI State") 


all_SVI <- c("SVI", "Census Tract", "SVI") 

all_SDI <- c("SDI", "Census Tract", "SDI") 





# Plot
data = matrix(c(all_EHR, EHR_1, EHR_2, EHR_3, EHR_4, EHR_5,
                all_SDOHD, SDOHD_1, SDOHD_2, SDOHD_3, SDOHD_4,
                all_EPA_AQS,
                all_ADI, ADI_1, ADI_2,
                all_SVI, 
                all_SDI
                ), ncol=3, byrow=TRUE)
 


# specify the column names and row names of matrix
colnames(data) = c("EHR Data", "SDOH Geographic Level (Granularity)", "Feature Set")

# assign to table
LT_table =as.data.table(data)


LT_table %>%
  kbl(caption="Breakdown of feature sets within EHR data and the five public SDOH databases",
       format= "latex",  booktabs = T,
   col.names = c("Data Type", "Geographic Level (Granularity)", "Feature Set"),
                  align="l",
                  digits = 3
   ) %>%
   kable_classic(full_width = FALSE, latex_options = "scale_down")


```


