---
title: "ahrq_clean_data_baselines"
output: html_notebook
---

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 


## Data prep:
orig_df: de-id patient data
AHRQ census tract data 2009-2020
```{r}
library(caret)
library(data.table)
library(dplyr)
library(sets)
library(scales)
library(tidyr)
library(stringr)

# Set wd when not in RStudio
setwd('__ PATH HERE __')

source('data_cleaners.R')

# Import patient dataset
orig_df <- read.csv("./__PATIENT DATA CSV HERE __")

# Import AHRQ data
ahrq_df_2009 <- read.csv("./TRACT_AHRQ/sdoh_2009_tract_1_0.csv")
ahrq_df_2010 <- read.csv("./TRACT_AHRQ/sdoh_2010_tract_1_0.csv") # header=FALSE
ahrq_df_2011 <- read.csv("./TRACT_AHRQ/sdoh_2011_tract_1_0.csv")
ahrq_df_2012 <- read.csv("./TRACT_AHRQ/sdoh_2012_tract_1_0.csv")
ahrq_df_2013 <- read.csv("./TRACT_AHRQ/sdoh_2013_tract_1_0.csv")
ahrq_df_2014 <- read.csv("./TRACT_AHRQ/sdoh_2014_tract_1_0.csv")
ahrq_df_2015 <- read.csv("./TRACT_AHRQ/sdoh_2015_tract_1_0.csv")
ahrq_df_2016 <- read.csv("./TRACT_AHRQ/sdoh_2016_tract_1_0.csv")
ahrq_df_2017 <- read.csv("./TRACT_AHRQ/sdoh_2017_tract_1_0.csv")
ahrq_df_2018 <- read.csv("./TRACT_AHRQ/sdoh_2018_tract_1_0.csv")
ahrq_df_2019 <- read.csv("./TRACT_AHRQ/sdoh_2019_tract_1_0.csv")
ahrq_df_2020 <- read.csv("./TRACT_AHRQ/sdoh_2020_tract_1_0.csv")


# Use fill to ensured consistent number of columns, merge dfs from 2009-2020 (via mean).
# Merge dfs on the 6 items below in list.
ahrq_total <- rbindlist(list(ahrq_df_2009, ahrq_df_2010, ahrq_df_2011, ahrq_df_2012, ahrq_df_2013,
                             ahrq_df_2014, ahrq_df_2015, ahrq_df_2016, ahrq_df_2017, ahrq_df_2018,
                             ahrq_df_2019, ahrq_df_2020), fill=TRUE)


# Import SVI Data: 
# SVI data download link & variable descriptions: https://www.atsdr.cdc.gov/placeandhealth/svi/data_documentation_download.html
setwd('__ PATH HERE __')

SVI_2014_US <- read.csv("./TRACT_AHRQ/SVI_2014_US.csv")
# Year: 2010. Geo level: census tract. All states in US included. 
# SVI_2010_US <- read.csv("SVI_2010_US.csv")



```

# Decide which AHRQ features to keep 
1. Keep all, divide into the 5 categories

```{r}
# Update ahrq_keep_cols with columns we want for features
# If census tract data: "TRACTFIPS": for census tract matching
# mean calculation is carried out via "TRACTFIPS" as well.

# Keep "COUNTYFIPS" for AQI merge.
# Keep "YEAR" for baselineyear merge.
ahrq_remove_cols <- c(
                 "STATEFIPS", "STATE", "COUNTY", "REGION", "TERRITORY", "CEN_AREALAND_SQM_TRACT", "CEN_POPDENSITY_TRACT", "ERS_RUCA1_2000", "ERS_RUCA2_2000", "ERS_RUCA1_2010", "ERS_RUCA2_2010", "CEN_AIAN_NH_IND")

ahrq_keep_cols <- names(ahrq_total)[! names(ahrq_total) %in% ahrq_remove_cols]

# Keep only 'ahrq_keep_cols'
ahrq_kept_feats = ahrq_total[, ..ahrq_keep_cols] # !(names(ahrq_total) %in% ahrq_remove_cols)]
head(ahrq_kept_feats)

```

# AHRQ imputation: fill NAs with median of feature wrt all census blocks in USA
# median

```{r}
impute_ahrq = names(subset(ahrq_kept_feats, select = -c(TRACTFIPS, COUNTYFIPS, YEAR)))
length(impute_ahrq) # Num features to impute on: 517 (ahrq, sdoh, and EPA air quality)
#impute_ahrq


median_ahrq_kept_feats <- ahrq_kept_feats

#sum <- 0
for (k in impute_ahrq) {
  
  median_ahrq_kept_feats[[k]][is.na(median_ahrq_kept_feats[[k]])] <- median(median_ahrq_kept_feats[[k]], na.rm = T)
  median_ahrq_kept_feats[[k]] <- rescale(median_ahrq_kept_feats[[k]]) # Rescale 0-1 with scale package
  
}



# Rename cols: tract_medianIMP prefix
med_names <- setdiff(colnames(median_ahrq_kept_feats), impute_ahrq)
median_ahrq_kept_feats <- median_ahrq_kept_feats %>% rename_at(vars(-one_of(med_names)), ~ paste0('tract_medianIMP_', .))



# Imp result: median_ahrq_kept_feats

```

# AHRQ imputation: fill NAs with mean of feature wrt all census blocks in USA
# mean

```{r}

impute_ahrq = names(subset(ahrq_kept_feats, select = -c(TRACTFIPS, COUNTYFIPS, YEAR)))
length(impute_ahrq) # Num features to impute on: 517 (ahrq, sdoh, and EPA air quality)
#impute_ahrq

mean_ahrq_kept_feats <- ahrq_kept_feats


#sum <- 0
for (k in impute_ahrq) {
  
  mean_ahrq_kept_feats[[k]][is.na(mean_ahrq_kept_feats[[k]])] <- median(mean_ahrq_kept_feats[[k]], na.rm = T)
  mean_ahrq_kept_feats[[k]] <- rescale(mean_ahrq_kept_feats[[k]]) # Rescale 0-1 with scale package
  
}



# Rename cols: tract_medianIMP prefix
mean_names <- setdiff(colnames(mean_ahrq_kept_feats), impute_ahrq)
mean_ahrq_kept_feats <- mean_ahrq_kept_feats %>% rename_at(vars(-one_of(mean_names)), ~ paste0('tract_meanIMP_', .))

# Imp result: mean_ahrq_kept_feats
```

# 1. AHRQ feature selection via 'baselineyear' year matching:

```{r}
head(median_ahrq_kept_feats)
```

# SVI Data: Separately prepare: 
```{r}
# Select desired variables from 'SVI_2014_US'
# SVI 2014 year variables meaning documented here: https://www.atsdr.cdc.gov/placeandhealth/svi/documentation/SVI_documentation_2010.html

# FIPS: census tract fips
# We don't keep the MOE columns (margin of error)



# E_: estimate using 2010-2014ACS data
svi_rawvars_keep_cols <- c("FIPS", "E_HU", "E_HH", "E_POV", "E_UNEMP", "E_PCI", 
                   "E_NOHSDP", "E_AGE65", "E_AGE17", "E_DISABL", "E_SNGPNT", 
                   "E_MINRTY", "E_LIMENG", "E_MUNIT", "E_MOBILE", "E_CROWD", 
                   "E_NOVEH", "E_GROUPQ")

# EP_: percentage
svi_percents_keep_cols <- c("EP_POV", "EP_UNEMP", "EP_PCI", "EP_NOHSDP", 
                            "EP_AGE65", "EP_AGE17", "EP_DISABL", "EP_SNGPNT", 
                            "EP_MINRTY", "EP_LIMENG", "EP_MUNIT", "EP_MOBILE", 
                            "EP_CROWD", "EP_NOVEH", "EP_GROUPQ")

svi_percentiles_keep_cols <- c( "EPL_POV", "EPL_UNEMP", "EPL_PCI", "EPL_NOHSDP",
        "EPL_AGE65", "EPL_AGE17", "EPL_DISABL", "EPL_SNGPNT",
        "EPL_MINRTY", "EPL_LIMENG", "EPL_MUNIT", "EPL_MOBILE",
        "EPL_CROWD", "EPL_NOVEH", "EPL_GROUPQ")

svi_RPL_raw_themes <- c("RPL_THEME1", "RPL_THEME2", "RPL_THEME3", "RPL_THEME4")

svi_composites_cols <- c("SPL_THEMES", "svi_RPL_raw_themes", "RPL_THEMES", "F_TOTAL")
# SVI_2014_US$SPL_THEMES # Sum of series 1 through 4 themes	
# SVI_2014_US$RPL_THEMES # Overall percentile ranking for themes 1 through 4
# SVI_2014_US$F_TOTAL # Sum of flags for the four themes	


svi_total_keep <- c(svi_rawvars_keep_cols, svi_percents_keep_cols, svi_percentiles_keep_cols, 
                    svi_RPL_raw_themes, svi_composites_cols)

SVI_2014_vars = SVI_2014_US[,(names(SVI_2014_US) %in% svi_total_keep)]

# Impute missing values with *median for that feature*: 
# NOTE: in SVI df, the CDC says: Values of -999 represent “null” or “no data.”
sum(SVI_2014_vars == "-999") # 2300 (of all counties. not yet matched to patients.)
sum(is.null(SVI_2014_vars))  # 0
sum(SVI_2014_vars == "no data") # 0

# So, for values == "-999" impute with median of column
# We see the following columns in SVI have 1 or more missing values (i.e. -999)
# [1] "E_PCI"
# [1] "EP_PCI"
# [1] "SPL_THEMES"
# [1] "RPL_THEMES"
# [1] "F_TOTAL"
imputed_SVI_2014_vars <- SVI_2014_vars
for(i in names(SVI_2014_vars)){
  imputed_SVI_2014_vars[[i]] <- sapply(SVI_2014_vars[,i],function(x) ifelse(x=="-999", median(SVI_2014_vars[,i], na.rm = TRUE), x))
}

SVI_2014_vars <- imputed_SVI_2014_vars # Un-alias. 
sum(SVI_2014_vars == "-999") # Now, no instances of -999.
```


# Separately prepare patient data:

```{r}
# Coerce NAs for patients without censustractcountynum OR census tract. 
# To allow head-to-head tract vs. county granularity comparison.
orig_df <- orig_df %>%
  mutate(censustract = as.numeric(censustract), na.rm=FALSE)

orig_df <- orig_df %>%
  mutate(countynum = as.numeric(countynum), na.rm=FALSE)

# Coerce NA for statenum. 
orig_df <- orig_df %>%
  mutate(statenum = as.numeric(statenum), na.rm=FALSE)

# First, remove rows in orig_df with an NA for any of the above: censustract, countynum, OR statenum
orig_df <- orig_df %>% drop_na(censustract)
orig_df <- orig_df %>% drop_na(countynum)
orig_df <- orig_df %>% drop_na(statenum)

# How many patients before removing GA?
nrow(orig_df) # 26030
# Only keep patients in GA (state = 13)
orig_df <- orig_df[orig_df$statenum == 13, ]
nrow(orig_df) # 33622: num ONLY in GA

table(orig_df$fips)  # County fips.





# do some cleaning
# keep:
# Patient_Home_Zip_Code
# Patient_Home_County
# "censustract"
# "baselineyear"

# Keep "countynum" (i.e. countyfips ) & "statenum"
remove_cols <- c("__ INSERT LIST OF PATIENT VARS TO REMOVE __")

orig_df = orig_df[,!(names(orig_df) %in% remove_cols)]

endpoints <- c("readmit30bin", "death30bin", "composite30")

# clean up the end-point related stuff
for (colx in endpoints) {
	orig_df <- remove_na(orig_df, colx)
}


# remove adi data
orig_df <- remove_na(orig_df, "ADI_national_rank")
orig_df <- create_folds(orig_df, endpoints)
write.csv(orig_df, file="./clean_tract.csv", row.names=FALSE) # clean_tract


## Age upper limit: remove patients with age_current > 100. 
# Before this, nrow = 44,142. After this, nrow = 44015. So 127 patients had age_current > 100.
orig_df <- orig_df[orig_df$age_current <= 100, ]

## fix it to be adults aged >= 18
orig_df <- orig_df[(orig_df$age_current >= 18), ]
orig_df <- create_folds(orig_df, endpoints)
write.csv(orig_df, file="./clean_tract_v1.csv", row.names=FALSE)


for (colx in c("Systolic_BP", "Heart_Rate", "Resp",
			   "loceuhfloor", "loceuhicu",
			   "loceclhfloor", "loceclhicu",
			   "specialcvd", "specialint",
			   "specialeme", "specialoth")) {
	orig_df <- remove_na(orig_df, colx)
}


orig_df <- remove_na(orig_df, "healthnT")

# CONSTRUCT "COUNTY_FIPS" column
# For later merging w county file.
# Convert County.Code to <chr> type from <dbl> 
orig_df <- transform(orig_df,
                             countynum = as.character(countynum))
# Convert County.Code to <chr> type from <int> 
orig_df <- transform(orig_df,
                             statenum = as.character(statenum))

# Pad county
orig_df[ ,'countynum'] <- str_pad(orig_df[,'countynum'], 3, pad = "0")
# Remove leading zero from state


# Now create the COUNTY_FIPS column via string concat
orig_df$COUNTY_FIPS <- str_c(orig_df$'statenum', '', orig_df$'countynum')
```



# Finally, combine 2 diff imp versions -- using cbind() columns. 
median_ahrq_kept_feats
mean_ahrq_kept_feats
```{r}

nrow(median_ahrq_kept_feats)
nrow(mean_ahrq_kept_feats)


# PERFORM MERGE: median & mean imps.
all_imps_ahrq <- merge(median_ahrq_kept_feats, mean_ahrq_kept_feats, by.x=c("TRACTFIPS", "YEAR"), by.y=c("TRACTFIPS", "YEAR"))
sum(is.na(all_imps_ahrq))

```

# Merge final AHRQ <-> patient final data:
# Also, merge SVI data (SVI_2014_vars)

```{r}
# - we have mean for each ahrq feature now <-> tractfips.
# colnames(orig_df)[colnames(orig_df) == 'censustract'] <- 'TRACTFIPS'
# Merge the dataframes based on matching values in 'TRACTFIPS' and 'YEAR' -- for baselineyear matching.

# Cast types to match:

# OPTION 1: Use census tract AHRQ data.
ahrq_baseline <- merge(all_imps_ahrq, orig_df, by.x=c("TRACTFIPS", "YEAR"), by.y=c("censustract", "baselineyear"))

ahrq_baseline <- merge(ahrq_baseline, SVI_2014_vars, by.x = "TRACTFIPS", by.y = "FIPS")

####################################################
```


