---
title: "ahrq_clean_data_baselines"
output: html_notebook
---

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 

```{r}
library(data.table)
library(dplyr)

# Set wd when not in RStudio
setwd('__ PATH HERE __')

```


# Input file: ahrq_censustract_feat_categories.csv
## contains total AHRQ features (for census tract), but needs to be deduplicated.

# Output file: ahrq_tract_categories_dedup.csv
## contains dedup TOTAL AHRQ features (for census tract) <-> feature category & domain.

both contain years: 2009 - 2020

```{r}
ahrq_tract_feat_cats <- read.csv("./ahrq_censustract_feat_categories.csv")
# Drop year col, to prepare for deduplicating 
ahrq_tract_feat_cats <- subset(ahrq_tract_feat_cats, select = -c(Year)) 
names(ahrq_tract_feat_cats)
nrow(ahrq_tract_feat_cats)

# Deduplicate rows, to have "Domain" and "SDOH_Topic" labels for each unique tract feature.
feats_dict <- ahrq_tract_feat_cats[!duplicated(ahrq_tract_feat_cats$Variable_Name), ]
nrow(dd_cats_check)

write.csv(feats_dict, file="./ahrq_tract_categories_dedup.csv", row.names=FALSE)


```





# Extra notes on data labeling inconsistencies in AHRQ : 

```{r}



# Deduplicate rows, to have "Domain" and "SDOH_Topic" labels for each feature.
dd_cats <- ahrq_tract_feat_cats[!duplicated(ahrq_tract_feat_cats), ]
nrow(dd_cats)

dd_cats_check <- ahrq_tract_feat_cats[!duplicated(ahrq_tract_feat_cats$Variable_Name), ]
nrow(dd_cats_check)

dd_cats[duplicated(dd_cats$Variable_Name), ]


# Example: why we filter ONLY on variable name, not Domain, SDOH_Topic, and Variable_Name.
selected_rows <- filter(dd_cats, Variable_Name == "HRSA_MUA_CENSUS_TRACT")
selected_rows


```

