---
title: "ahrq_clean_data_baselines"
output: html_notebook
---

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 



## Data prep:
orig_df: de-id patient data
AHRQ census tract data 2009-2020
```{r}
library(caret)
library(data.table)
library(dplyr)
library(sets)
library(scales)
library(tidyr)
library(stringr)



# State plotting
library(usmap)
library(sf)
library(rio)  
library(sp) # Dependency
library(maps)

# Set wd when not in RStudio
setwd('__ PATH HERE __')

source('data_cleaners.R')

# Import patient dataset
orig_df <- read.csv("./__ PATIENT DATASET CSV HERE __")


# Import AHRQ data
ahrq_df_2009 <- read.csv("./COUNTY_AHRQ/SDOH_2009_COUNTY_1_0.csv")
ahrq_df_2010 <- read.csv("./COUNTY_AHRQ/SDOH_2010_COUNTY_1_0.csv") # header=FALSE
ahrq_df_2011 <- read.csv("./COUNTY_AHRQ/SDOH_2011_COUNTY_1_0.csv") # header=FALSE
ahrq_df_2012 <- read.csv("./COUNTY_AHRQ/SDOH_2012_COUNTY_1_0.csv") # header=FALSE
ahrq_df_2013 <- read.csv("./COUNTY_AHRQ/SDOH_2013_COUNTY_1_0.csv") # header=FALSE
ahrq_df_2014 <- read.csv("./COUNTY_AHRQ/SDOH_2014_COUNTY_1_0.csv") # header=FALSE
ahrq_df_2015 <- read.csv("./COUNTY_AHRQ/SDOH_2015_COUNTY_1_0.csv") # header=FALSE
ahrq_df_2016 <- read.csv("./COUNTY_AHRQ/SDOH_2016_COUNTY_1_0.csv") # header=FALSE
ahrq_df_2017 <- read.csv("./COUNTY_AHRQ/SDOH_2017_COUNTY_1_0.csv") # header=FALSE
ahrq_df_2018 <- read.csv("./COUNTY_AHRQ/SDOH_2018_COUNTY_1_1.csv") # header=FALSE
ahrq_df_2019 <- read.csv("./COUNTY_AHRQ/SDOH_2019_COUNTY_1_0.csv") # header=FALSE
ahrq_df_2020 <- read.csv("./COUNTY_AHRQ/SDOH_2020_COUNTY_1_0.csv") # header=FALSE




# Use fill to ensured consistent number of columns, merge dfs from 2009-2020 (via mean).
# Merge dfs on the 6 items below in list.
ahrq_total <- rbindlist(list(ahrq_df_2009, ahrq_df_2010, ahrq_df_2011, ahrq_df_2012, ahrq_df_2013,
                             ahrq_df_2014, ahrq_df_2015, ahrq_df_2016, ahrq_df_2017, ahrq_df_2018,
                             ahrq_df_2019, ahrq_df_2020), fill=TRUE)


```

# Decide which AHRQ features to keep 
1. Keep all, divide into the 5 categories

```{r}
# Update ahrq_keep_cols with columns we want for features
# If census tract data: "COUNTYFIPS": for census tract matching
# median calculation is carried out via "COUNTYFIPS" as well.

# Keep "COUNTYFIPS" for AQI merge.
# Keep "YEAR" for baselineyear merge.
# Remove all feats from "Geography" cat 6.
ahrq_remove_cols <- c(
                 "STATEFIPS", "STATE", "COUNTY", "REGION", "TERRITORY", 
                 "AHRF_USDA_RUCC_2013", 
                 "CEN_AREALAND_SQM_COUNTY",
                  "CEN_POPDENSITY_COUNTY",
                 "NCHS_URCS_2006",
                  "NCHS_URCS_2013")


# Preserve these columns, but do NOT impute.
  
county_neighbors_cols <- c("CAF_ADJ_COUNTY_1",
 "CAF_ADJ_COUNTY_2",
 "CAF_ADJ_COUNTY_3",
 "CAF_ADJ_COUNTY_4",
 "CAF_ADJ_COUNTY_5",
 "CAF_ADJ_COUNTY_6",
 "CAF_ADJ_COUNTY_7",
 "CAF_ADJ_COUNTY_8",
 "CAF_ADJ_COUNTY_9",
 "CAF_ADJ_COUNTY_10",
 "CAF_ADJ_COUNTY_11",
 "CAF_ADJ_COUNTY_12",
 "CAF_ADJ_COUNTY_13",
 "CAF_ADJ_COUNTY_14")


ahrq_keep_cols <- names(ahrq_total)[! names(ahrq_total) %in% ahrq_remove_cols]

# Keep only 'ahrq_keep_cols'
ahrq_kept_feats <- ahrq_total[, ..ahrq_keep_cols] # !(names(ahrq_total) %in% ahrq_remove_cols)]

# Set aside 'county_neighbors_cols' columns, but do NOT impute.
#saved_spatial_ahrq_total <- ahrq_total


```

# AHRQ imputation: fill NAs with median of feature wrt all counties in USA
- 1. ** Median (using this cell, naming: medianIMP_...)
- 2. Mean
- 3. Spatial (via county_neighbor_cols)

Note: always begin with ahrq_kept_feats, then append cols to 'impute_ahrq'. 
- impute_ahrq will hold 3 diff versions of imputation for AQI feats.

```{r}
# Impute all columns EXCEPT 'impute_ahrq' list.
impute_ahrq = names(subset(ahrq_kept_feats, select = -c(COUNTYFIPS, YEAR, CAF_ADJ_COUNTY_1,
CAF_ADJ_COUNTY_2,
CAF_ADJ_COUNTY_3,
CAF_ADJ_COUNTY_4,
CAF_ADJ_COUNTY_5,
CAF_ADJ_COUNTY_6,
CAF_ADJ_COUNTY_7,
CAF_ADJ_COUNTY_8,
CAF_ADJ_COUNTY_9,
CAF_ADJ_COUNTY_10,
CAF_ADJ_COUNTY_11,
CAF_ADJ_COUNTY_12,
CAF_ADJ_COUNTY_13,
CAF_ADJ_COUNTY_14)))

# length(impute_ahrq) # Num features to impute on: 517 (ahrq, sdoh, and EPA air quality)

# MEDIAN IMP results
med_ahrq_kept_feats <- ahrq_total[, ..ahrq_keep_cols] # !(names(ahrq_total) %in% ahrq_remove_cols)]



# IMPUTE COLS: names of cols are 'impute_ahrq'
# imputed df is 'ahrq_kept_feats'
# We use ahrq_total for inpute to imp. (since not yet updated w imps.)

for (k in impute_ahrq) {
  # First, DROP ahrq col if col has >50% NAs (ie. >50% patients don't have the feat value)
  
  #if( (sum(is.na(merged_df[[k]]))/nrow(merged_df)) >= 0.5 ){
    # TODO: in future, drop these feats, but for now it causes issues with JSON feat groups.
    # merged_df = select(merged_df, -k ) # Drop feat col if >50% missing.
    # For now, just replace feat val with 0s for ALL patients (so we pass true)
    #merged_df[[k]] <- replace(merged_df[[k]], TRUE, 0) 
    #print(length(merged_df[[k]]))
    #sum = sum +1
  #}
  med_ahrq_kept_feats[[k]][is.na(med_ahrq_kept_feats[[k]])] <- median(ahrq_total[[k]], na.rm = T)
  med_ahrq_kept_feats[[k]] <- rescale(med_ahrq_kept_feats[[k]]) # Rescale 0-1 with scale package
  
}


# Rename cols: county_medianIMP prefix
med_names <- setdiff(colnames(med_ahrq_kept_feats), impute_ahrq)
med_ahrq_kept_feats <- med_ahrq_kept_feats %>% rename_at(vars(-one_of(med_names)), ~ paste0('county_medianIMP_', .))


# names(med_ahrq_kept_feats)
med_ahrq_kept_feats <- data.frame(med_ahrq_kept_feats)
```


# AHRQ imputation: 
- 1.  Median 
- 2. ** Mean (using this cell, naming: meanIMP_...)
- 3. Spatial (via county_neighbor_cols)
```{r}
impute_ahrq = names(subset(ahrq_kept_feats, select = -c(COUNTYFIPS, YEAR, CAF_ADJ_COUNTY_1,
CAF_ADJ_COUNTY_2,
CAF_ADJ_COUNTY_3,
CAF_ADJ_COUNTY_4,
CAF_ADJ_COUNTY_5,
CAF_ADJ_COUNTY_6,
CAF_ADJ_COUNTY_7,
CAF_ADJ_COUNTY_8,
CAF_ADJ_COUNTY_9,
CAF_ADJ_COUNTY_10,
CAF_ADJ_COUNTY_11,
CAF_ADJ_COUNTY_12,
CAF_ADJ_COUNTY_13,
CAF_ADJ_COUNTY_14)))

# length(impute_ahrq) # Num features to impute on: 517 (ahrq, sdoh, and EPA air quality)

# MEDIAN IMP results
mean_ahrq_kept_feats <- ahrq_total[, ..ahrq_keep_cols] # !(names(ahrq_total) %in% ahrq_remove_cols)]



# IMPUTE COLS: names of cols are 'impute_ahrq'
# imputed df is 'ahrq_kept_feats'
# We use ahrq_total for inpute to imp. (since not yet updated w imps.)

for (k in impute_ahrq) {

  mean_ahrq_kept_feats[[k]][is.na(mean_ahrq_kept_feats[[k]])] <- mean(ahrq_total[[k]], na.rm = T)
  mean_ahrq_kept_feats[[k]] <- rescale(mean_ahrq_kept_feats[[k]]) # Rescale 0-1 with scale package
  
}


# Rename cols: county_meanIMP prefix
med_names <- setdiff(colnames(mean_ahrq_kept_feats), impute_ahrq)
mean_ahrq_kept_feats <- mean_ahrq_kept_feats %>% rename_at(vars(-one_of(med_names)), ~ paste0('county_meanIMP_', .))


#names(mean_ahrq_kept_feats)
mean_ahrq_kept_feats <- data.frame(mean_ahrq_kept_feats)
```


# Create EPAA AQS: columns by year (instead of year rows)

```{r}
AQI_w_FIPS <- names(subset(ahrq_total, select = c(COUNTYFIPS, STATEFIPS, YEAR, 
                                                  EPAA_2NDMAX_CO_1HR,
                                                  EPAA_2NDMAX_CO_8HR,
                                                  EPAA_98PR_NO2_1HR,
                                                  EPAA_MEAN_NO2_1HR,
                                                  EPAA_2NDMAX_O3_1HR,
                                                  EPAA_4THMAX_O3_8HR,
                                                  EPAA_MAX_PB_3MON,
                                                  EPAA_2NDMAX_PM10_24HR,
                                                  EPAA_MEAN_WTD_PM10,
                                                  EPAA_MEAN_WTD_PM25,
                                                  EPAA_98PR_PM25_DAILY,
                                                  EPAA_99PR_SO2_1HR,
                                                  EPAA_2NDMAX_SO2_24HR,
                                                  EPAA_MEAN_SO2_1HR
                                                  )))


AQI_w_FIPS <- ahrq_total[ , ..AQI_w_FIPS] # Air cols + County identifier col.


# Showing AQI features from 2009-2020 as columns. Each FIPS is a unique row. Years along columns.
aqi_wide <- AQI_w_FIPS %>%
  pivot_wider(
    id_cols = c(COUNTYFIPS, STATEFIPS),
    names_from = YEAR,
    values_from = c(EPAA_2NDMAX_CO_1HR,
                    EPAA_2NDMAX_CO_8HR,
                    EPAA_98PR_NO2_1HR,
                    EPAA_MEAN_NO2_1HR,
                    EPAA_2NDMAX_O3_1HR,
                    EPAA_4THMAX_O3_8HR,
                    EPAA_MAX_PB_3MON,
                    EPAA_2NDMAX_PM10_24HR,
                    EPAA_MEAN_WTD_PM10,
                    EPAA_MEAN_WTD_PM25,
                    EPAA_98PR_PM25_DAILY,
                    EPAA_99PR_SO2_1HR,
                    EPAA_2NDMAX_SO2_24HR,
                    EPAA_MEAN_SO2_1HR),
    names_sep = "."
  ) %>%
  arrange(COUNTYFIPS)

aqi_wide <- aqi_wide %>% drop_na(COUNTYFIPS)

aqi_wide

# Do right join because wide_county_fips_to_name is ground truth.

# Do string matching: County to County_Name, State to State_Abbrev

# Also Creates new County_FIPS column

AQI_w_FIPS <- aqi_wide %>% select(COUNTYFIPS, everything()) # Move County_FIPS to be first column



res <- (sum(is.na(AQI_w_FIPS$EPAA_MEAN_WTD_PM25.2009))+sum(is.na(AQI_w_FIPS$EPAA_MEAN_WTD_PM25.2010))+sum(is.na(AQI_w_FIPS$EPAA_MEAN_WTD_PM25.2011))+sum(is.na(AQI_w_FIPS$EPAA_MEAN_WTD_PM25.2012))+sum(is.na(AQI_w_FIPS$EPAA_MEAN_WTD_PM25.2013))+sum(is.na(AQI_w_FIPS$EPAA_MEAN_WTD_PM25.2014))+sum(is.na(AQI_w_FIPS$EPAA_MEAN_WTD_PM25.2015))+sum(is.na(AQI_w_FIPS$EPAA_MEAN_WTD_PM25.2016))+sum(is.na(AQI_w_FIPS$EPAA_MEAN_WTD_PM25.2017))+sum(is.na(AQI_w_FIPS$EPAA_MEAN_WTD_PM25.2018))+sum(is.na(AQI_w_FIPS$EPAA_MEAN_WTD_PM25.2019))+sum(is.na(AQI_w_FIPS$EPAA_MEAN_WTD_PM25.2020)))
```


```{r}

# Plot "after" Median Imputation
# Plot example is for Georgia (GA)

#med_ahrq_kept_feats$county_medianIMP_EPAA_MEAN_WTD_PM25
ahrq_epa_median_2010 <- med_ahrq_kept_feats[med_ahrq_kept_feats$YEAR == 2010,]
ahrq_epa_median_2010 <- subset(ahrq_epa_median_2010, select = c("COUNTYFIPS", "county_medianIMP_EPAA_MEAN_WTD_PM25"))






d   <- us_map("counties")
d   <- d[d$abbr == "GA",]
GAc <- lapply(split(d, d$county), function(x) st_polygon(list(cbind(x$x, x$y))))
GA  <- st_sfc(GAc, crs = usmap_crs()@projargs)
GA  <- st_sf(data.frame(fips = unique(d$fips), county = names(GAc), geometry = GA))


GA_aqi_2009 <- ahrq_epa_median_2010 # Copy for plot


colnames(GA_aqi_2009) <-  c("fips", "county_medianIMP_EPAA_MEAN_WTD_PM25")

# Weighted annual mean (mean weighted by calendar quarter) for the year of PM2.5 (ug/m3)

# PLOT HERE IS AFTER MEDIAN IMPUTATION
plot_usmap( data = GA_aqi_2009, values = "county_medianIMP_EPAA_MEAN_WTD_PM25", "counties", include = c("GA"), color="black") +  
    labs(title="")+  
    scale_fill_continuous(low = "#56B1F7", high = "#132B43", name="2010: Mean PM2.5 (ug/m3)", label=scales::comma)+  
    theme(plot.background=element_rect(), legend.position="right")  +
    theme(plot.background = element_rect(color=NA, fill = "white"),
             panel.background = element_rect(color=NA, fill = "white"))

```



# Total county AQI data: 
```{r}
# Drop STATEFIPS column
# Before spatial imputation.
write.csv(AQI_w_FIPS, "./totalCounty_AHRQ_EPAA_by_FIPS_beforeimputation.csv", row.names=FALSE)

```

# Use state of Georgia as an example: Georgia (GA) only
```{r}

# We could take Only take State == 13 (GA).
# state_AQI_w_FIPS <- AQI_w_FIPS[AQI_w_FIPS$STATEFIPS == "13", ]

# However, we decide to keep all states becuase some feats have no values just in GA.
# So we preserve these feats instead of dropping them.


# Drop STATEFIPS column
#state_AQI_w_FIPS <- subset(state_AQI_w_FIPS, select=-c(STATEFIPS))
#state_AQI_w_FIPS

#write.csv(state_AQI_w_FIPS, "./GAstateCounty_AHRQ_EPAA_beforeimputation.csv", row.names=FALSE)
```



```{r}



```

# Spatial AQS Imputation
impute upon *AQI_w_FIPS*, using county_adj as the guide to know which FIPS are neighbors.
For all imputation approaches, we aim to reach a full matrix of AQI features for all counties. 
The full matrix is required in order to have values for each year for each location, as the 'baseline year' feature experiments may require AQI features from a single year in a county, instead of averaging a county AQI features over years 2009-2020.

```{r}
# Read in the FIPS adjacency file (created above)
#county_adj <- read.csv(file='county_adjacency_clean.csv')
AQI_w_FIPS <- read.csv(file='totalCounty_AHRQ_EPAA_by_FIPS_beforeimputation.csv') # Not only GA state, bc some feats are completely NA.
county_adj_cols <- names(subset(ahrq_kept_feats, select = c(COUNTYFIPS, CAF_ADJ_COUNTY_1,
CAF_ADJ_COUNTY_2,
CAF_ADJ_COUNTY_3,
CAF_ADJ_COUNTY_4,
CAF_ADJ_COUNTY_5,
CAF_ADJ_COUNTY_6,
CAF_ADJ_COUNTY_7,
CAF_ADJ_COUNTY_8,
CAF_ADJ_COUNTY_9,
CAF_ADJ_COUNTY_10,
CAF_ADJ_COUNTY_11,
CAF_ADJ_COUNTY_12,
CAF_ADJ_COUNTY_13,
CAF_ADJ_COUNTY_14)))


county_adj <-  ahrq_total[ , ..county_adj_cols]


############ 1.1 Simple spatial imputation (iterate & repeat until fully imputed.)
# (1.1) We use mean for spatial imputation because we assume the features have a normal dist among neighbors. 

# Below, we will do spatial imputation. 
# This means, for a given COUNTYFIPS (i.e. row): if a missing value exists.
imp_1_AQI_by_FIPS <-  AQI_w_FIPS

nrow(imp_1_AQI_by_FIPS)
sum(is.na(imp_1_AQI_by_FIPS$EPAA_2NDMAX_CO_1HR.2016))
```


# Plot "before" of AHRQ EPA feats:
# for example, in GA:
```{r}
AQI_w_FIPS

d   <- us_map("counties")
d   <- d[d$abbr == "GA",]
GAc <- lapply(split(d, d$county), function(x) st_polygon(list(cbind(x$x, x$y))))
GA  <- st_sfc(GAc, crs = usmap_crs()@projargs)
GA  <- st_sf(data.frame(fips = unique(d$fips), county = names(GAc), geometry = GA))


GA_aqi_2009 <- subset(AQI_w_FIPS, select = c("COUNTYFIPS", "EPAA_MEAN_WTD_PM25.2010"))


colnames(GA_aqi_2009) <-  c("fips", "EPAA_MEAN_WTD_PM25.2010")

# Weighted annual mean (mean weighted by calendar quarter) for the year of PM2.5 (ug/m3)

# PLOT HERE IS BEFORE ANY IMPUTATION
plot_usmap( data = GA_aqi_2009, values = "EPAA_MEAN_WTD_PM25.2010", "counties", include = c("GA"), color="black") +  
    labs(title="")+  
    scale_fill_continuous(low = "#56B1F7", high = "#132B43", name="2010: Mean PM2.5 (ug/m3)", label=scales::comma)+  
    theme(plot.background=element_rect(), legend.position="right")  +
    theme(plot.background = element_rect(color=NA, fill = "white"),
             panel.background = element_rect(color=NA, fill = "white"))


```




```{r}
# Read in the FIPS adjacency file (created above)
setwd('__ PATH HERE __')


county_adj <- read.csv(file='./TRACT_AHRQ/county_adjacency_clean.csv')

imp_1_AQI_by_FIPS <-  AQI_w_FIPS

cols <- setdiff(names(AQI_w_FIPS), c("COUNTYFIPS", "YEAR")) # Air cols we impute on.
  
impute_AQI_iterate <- function(imp_1_AQI_by_FIPS, cols) {
  failed_imp <- 0 # To count num where neighbors didn't have any vals for that feature to impute.
  # Iterate across columns
  for (i in seq_along(cols)){
    #prevcol <- cols[i-1]
    thiscol <- cols[i]
    curr_year <- sub(".*\\.(\\d+)$", "\\1", thiscol)
    print(curr_year)
    # This loop goes down the column
    for(j in seq_along(imp_1_AQI_by_FIPS[[thiscol]])){
      cell_val <- imp_1_AQI_by_FIPS[j, thiscol][1] 
      if(is.na(cell_val)){
        #print(cell_val)
        curr_FIPS <- imp_1_AQI_by_FIPS[j, "COUNTYFIPS"]
        #print(curr_FIPS)
        neighs <- as.list(county_adj[county_adj$FIPS_key == curr_FIPS,])
        neighs <- unname(neighs) # Removes column names from neighbor list.
        if(length(neighs) > 0){
          neighs <- as.list( neighs[2 : length(neighs)] ) # Drop first list elmnt (i.e. the key)
        }
        # print(neighs)
        # Now take mean of neighbor feat vals: for 'thiscol'
        imp_cell <- imp_1_AQI_by_FIPS[imp_1_AQI_by_FIPS$COUNTYFIPS %in% neighs,][thiscol] 
        imp_cell <- imp_cell[!is.na(imp_cell)]
        if(length(imp_cell) > 0 ){
          imp_cell <- mean(imp_cell)
        }
        
  
        # If NA, then imp_cell length is 0.
        if(length(imp_cell) > 0){
          imp_1_AQI_by_FIPS[j, thiscol] <- imp_cell
        }
        else{
          failed_imp = failed_imp + 1
        }
        #print(imp_cell)
      }
    }
  }
  
  return(imp_1_AQI_by_FIPS)
} # End function

# Track num left to impute (for each feature)
imp_runs = 6

cols_num_still_NA <- data.frame(matrix(ncol = length(cols), nrow = (imp_runs+1) ))
colnames(cols_num_still_NA) <- cols
# Get initial number needed to impute (before ANY imputation).
num_NAs_left <- sapply(imp_1_AQI_by_FIPS, function(x) sum(is.na(x)))
cols_num_still_NA[1,] <- num_NAs_left  # Add row for num NAs in each column of 'imp_1_AQI_by_FIPS'


# Perform imputation over 'imp_runs' num of iterations 
for(i in 1:imp_runs){
  # run imp
  imp_1_AQI_by_FIPS <- impute_AQI_iterate(imp_1_AQI_by_FIPS, cols)
  print(sum(is.na(imp_1_AQI_by_FIPS)))
  
  # If after 1st iterationAdd row for num NAs in each column of 'imp_1_AQI_by_FIPS'
  num_NAs_left <- sapply(imp_1_AQI_by_FIPS, function(x) sum(is.na(x)))
  cols_num_still_NA[i + 1,] <- num_NAs_left
}
  

cols_num_still_NA # num iterations = nrows -1 

# Temporarily remove spatial identifiers for renaming columns
cols <- setdiff(names(imp_1_AQI_by_FIPS), c("COUNTYFIPS"))
imp_1_AQI_by_FIPS <- subset(imp_1_AQI_by_FIPS, select = cols)

# Rename all feats to indicate SPATIAL imp was done:
# No need to indicate county. All air quality data are county (either AHRQ EPAA or EPA AQS.)
colnames(imp_1_AQI_by_FIPS) <- paste("AHRQ_spatialIMP", colnames(imp_1_AQI_by_FIPS), sep = ".")

imp_1_AQI_by_FIPS

# Bring back in c("COUNTYFIPS")
COUNTYFIPS <- AQI_w_FIPS$COUNTYFIPS

imp_1_AQI_by_FIPS <- cbind(imp_1_AQI_by_FIPS, COUNTYFIPS) 


# Shows just in GA, 2 features/columns have no data at all.
#names(imp_1_AQI_by_FIPS)[sapply(imp_1_AQI_by_FIPS, function(x) sum(is.na(x)) == length(x))]


sum(is.na(imp_1_AQI_by_FIPS)) # Ideally until no NAs. 
write.csv(imp_1_AQI_by_FIPS, file="./AHRQ_EPAA_final_spatial_imp_1.csv", row.names = FALSE )
```

# Plot after spatial imp
# Use GA state as example
```{r}

AQI_w_FIPS

d   <- us_map("counties")
d   <- d[d$abbr == "GA",]
GAc <- lapply(split(d, d$county), function(x) st_polygon(list(cbind(x$x, x$y))))
GA  <- st_sfc(GAc, crs = usmap_crs()@projargs)
GA  <- st_sf(data.frame(fips = unique(d$fips), county = names(GAc), geometry = GA))


GA_aqi_2009 <- subset(imp_1_AQI_by_FIPS, select = c("COUNTYFIPS", "AHRQ_spatialIMP.EPAA_MEAN_WTD_PM25.2010"))


colnames(GA_aqi_2009) <-  c("fips", "AHRQ_spatialIMP.EPAA_MEAN_WTD_PM25.2010")


# PLOT AFTER SPATIAL IMPUTATION
plot_usmap( data = GA_aqi_2009, values = "AHRQ_spatialIMP.EPAA_MEAN_WTD_PM25.2010", "counties", include = c("GA"), color="black") +  
    labs(title="")+  
    scale_fill_continuous(low = "#56B1F7", high = "#132B43", name="2010: Mean PM2.5 (ug/m3)", label=scales::comma)+  
    theme(plot.background=element_rect(), legend.position="right") +
      theme(plot.background = element_rect(color=NA, fill = "white"),
             panel.background = element_rect(color=NA, fill = "white"))

```


# Finally, combine 2 diff imp versions -- using cbind() columns. 
median_ahrq_kept_feats
mean_ahrq_kept_feats
( keep in separate file: spatial_ahrq_kept_feats: "AHRQ_EPAA_final_spatial_imp_1.csv")

```{r}
# Note: ahrq_kept_feats has pre-imputation version. 
# ----- Merge these 2 (on COUNTYFIPS)
# We store 'imp_1_AQI_by_FIPS' in a separate file.
nrow(med_ahrq_kept_feats) # COUNTYFIPS
nrow(mean_ahrq_kept_feats)
#nrow(imp_1_AQI_by_FIPS)

# Drop the adjacent county columns: 
county_neighbors_cols <- c("CAF_ADJ_COUNTY_1",
 "CAF_ADJ_COUNTY_2",
 "CAF_ADJ_COUNTY_3",
 "CAF_ADJ_COUNTY_4",
 "CAF_ADJ_COUNTY_5",
 "CAF_ADJ_COUNTY_6",
 "CAF_ADJ_COUNTY_7",
 "CAF_ADJ_COUNTY_8",
 "CAF_ADJ_COUNTY_9",
 "CAF_ADJ_COUNTY_10",
 "CAF_ADJ_COUNTY_11",
 "CAF_ADJ_COUNTY_12",
 "CAF_ADJ_COUNTY_13",
 "CAF_ADJ_COUNTY_14")


med_keep_cols <- names(med_ahrq_kept_feats)[! names(med_ahrq_kept_feats) %in% county_neighbors_cols]
mean_keep_cols <- names(mean_ahrq_kept_feats)[! names(mean_ahrq_kept_feats) %in% county_neighbors_cols]

# Subset cols.
med_ahrq_kept_feats <- med_ahrq_kept_feats[, med_keep_cols]
mean_ahrq_kept_feats <- mean_ahrq_kept_feats[, mean_keep_cols]



# PERFORM MERGE: median & mean imps.
all_imps_ahrq <- merge(med_ahrq_kept_feats, mean_ahrq_kept_feats, by.x=c("COUNTYFIPS", "YEAR"), by.y=c("COUNTYFIPS", "YEAR"))
sum(is.na(all_imps_ahrq))

```

# 1. AHRQ feature selection via 'baselineyear' year matching:

```{r}
head(all_imps_ahrq)
```



# Separately prepare patient data:

```{r}

# Coerce NAs for patients without countynum OR census tract. 
# To allow head-to-head tract vs. county granularity comparison.
orig_df <- orig_df %>%
  mutate(censustract = as.numeric(censustract), na.rm=FALSE)

orig_df <- orig_df %>%
  mutate(countynum = as.numeric(countynum), na.rm=FALSE)

# Coerce NA for statenum. 
orig_df <- orig_df %>%
  mutate(statenum = as.numeric(statenum), na.rm=FALSE)

# First, remove rows in orig_df with an NA for any of the above: censustract, countynum, OR statenum
orig_df <- orig_df %>% drop_na(censustract)
orig_df <- orig_df %>% drop_na(countynum)
orig_df <- orig_df %>% drop_na(statenum)

# How many patients before removing GA?
nrow(orig_df) # 26030
# Only keep patients in GA (state = 13)
orig_df <- orig_df[orig_df$statenum == 13, ]
nrow(orig_df) # 33622: num ONLY in GA

table(orig_df$fips)  # County fips.



# do some cleaning
# keep:
# Patient_Home_Zip_Code
# Patient_Home_County
# "censustract"
# "baselineyear"

# keep "fips", which is county fips.
remove_cols <- c("__ cols to remove from patient dataset __")

orig_df = orig_df[,!(names(orig_df) %in% remove_cols)]

endpoints <- c("readmit30bin", "death30bin", "composite30")

# clean up the end-point related stuff
for (colx in endpoints) {
	orig_df <- remove_na(orig_df, colx)
}


# remove adi data
orig_df <- remove_na(orig_df, "ADI_national_rank")
orig_df <- create_folds(orig_df, endpoints)
write.csv(orig_df, file="./clean_tract.csv", row.names=FALSE) # clean_tract


## Age upper limit: remove patients with age_current > 100. 
# Before this, nrow = 44,142. After this, nrow = 44015. So 127 patients had age_current > 100.
orig_df <- orig_df[orig_df$age_current <= 100, ]

## fix it to be adults aged >= 18
orig_df <- orig_df[(orig_df$age_current >= 18), ]
orig_df <- create_folds(orig_df, endpoints)
write.csv(orig_df, file="./clean_tract_v1.csv", row.names=FALSE)


for (colx in c("Systolic_BP", "Heart_Rate", "Resp",
			   "loceuhfloor", "loceuhicu",
			   "loceclhfloor", "loceclhicu",
			   "specialcvd", "specialint",
			   "specialeme", "specialoth")) {
	orig_df <- remove_na(orig_df, colx)
}

orig_df <- remove_na(orig_df, "healthnT")


nrow(orig_df) # Num patients: 30702
```

# Merge final AHRQ <-> patient final data:

```{r}
# - we have mean for each ahrq feature now <-> tractfips.
# colnames(orig_df)[colnames(orig_df) == 'censustract'] <- 'TRACTFIPS'
# Merge the dataframes based on matching values in 'TRACTFIPS' and 'YEAR' -- for baselineyear matching.

# Cast types to match:

# OPTION 1: Use census tract AHRQ data.
# ahrq_baseline <- merge(ahrq_kept_feats, orig_df, by.x=c("TRACTFIPS", "YEAR"), by.y=c("censustract", "baselineyear"))

# (what we use) OPTION 2: Use *county* AHRQ data.
ahrq_baseline <- merge(all_imps_ahrq, orig_df, by.x=c("COUNTYFIPS", "YEAR"), by.y=c("fips", "baselineyear"))



#ahrq_baseline <- merge(ahrq_baseline, SVI_2014_vars, by.x = "TRACTFIPS", by.y = "FIPS")

####################################################
```

