---
title: "AHRQ Clean Data: for census tract features (NAs, or imputation)"
output: html_notebook
---

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 



## Data prep:
- orig_df: de-id patient data
- AHRQ census tract data 2009-2020

# Challenge with EPA AQS: the air quality data file only lists the county name... not a FIPS number. 
- link: EPA AQS leveled state,county ranking: https://aqs.epa.gov/aqsweb/documents/codetables/states_and_counties.html
- Build COUNTY_FIPS field in AQI dataset: 
    - "first two digits represent the county's state and the last three digits represent the county"
    - perform: COUNTY_FIPS = string(state code) + string(county code)


# Do *iterative* spatial imputation in this file. Ideally better than 1 pass followed by feat mean imputation.
```{r}
library(caret)
library(data.table)
library(dplyr)
library(sets)
library(scales)
library(tidyr)
library(tidyverse)
library(stringr)
library(purrr)
library(zoo) # Imputation help
library(stringr)


# State plotting
library(usmap)
library(sf)
library(rio)  
library(sp) # Dependency
library(maps)


# Imputation: 
library(multiUS)
library(imputeMulti)
library("mice")


# Set wd when not in RStudio
setwd('__ PATH HERE __')

source('data_cleaners.R')

orig_df <- read.csv("./__ PATIENT DATASET CSV HERE__")

aqi_df_2009 <- read.csv("./TRACT_AHRQ/annual_aqi_by_county_2009.csv")
aqi_df_2010 <- read.csv("./TRACT_AHRQ/annual_aqi_by_county_2010.csv")
aqi_df_2011 <- read.csv("./TRACT_AHRQ/annual_aqi_by_county_2011.csv")
aqi_df_2012 <- read.csv("./TRACT_AHRQ/annual_aqi_by_county_2012.csv")
aqi_df_2013 <- read.csv("./TRACT_AHRQ/annual_aqi_by_county_2013.csv")
aqi_df_2014 <- read.csv("./TRACT_AHRQ/annual_aqi_by_county_2014.csv")
aqi_df_2015 <- read.csv("./TRACT_AHRQ/annual_aqi_by_county_2015.csv")
aqi_df_2016 <- read.csv("./TRACT_AHRQ/annual_aqi_by_county_2016.csv")
aqi_df_2017 <- read.csv("./TRACT_AHRQ/annual_aqi_by_county_2017.csv")
aqi_df_2018 <- read.csv("./TRACT_AHRQ/annual_aqi_by_county_2018.csv")
aqi_df_2019 <- read.csv("./TRACT_AHRQ/annual_aqi_by_county_2019.csv")
aqi_df_2020 <- read.csv("./TRACT_AHRQ/annual_aqi_by_county_2020.csv")

aqi_total <- rbindlist(list(aqi_df_2009, aqi_df_2010, aqi_df_2011, aqi_df_2012, aqi_df_2013, 
                            aqi_df_2014, aqi_df_2015, aqi_df_2016, aqi_df_2017, aqi_df_2018, 
                            aqi_df_2019, aqi_df_2020), fill=TRUE)

# EPA AQS: state + county code matching (via state, county name)
epa_counties <- read.csv("./TRACT_AHRQ/states_and_counties.csv") # Has names, state code, county code.


```


# First, make an EPA COUNTY_FIPS code using state + county.

```{r}


# Convert County.Code to <chr> type from <int> 
epa_counties <- transform(epa_counties,
                             County.Code = as.character(County.Code))

# Pad county
epa_counties[ ,'County.Code'] <- str_pad(epa_counties[,'County.Code'], 3, pad = "0")
# Remove leading zero from state
epa_counties[ ,'State.Code'] <- str_remove(epa_counties[,'State.Code'], "^0+")

# Now create the COUNTY_FIPS column via string concat
epa_counties$COUNTY_FIPS <- str_c(epa_counties$'State.Code', '', epa_counties$'County.Code')

# Keep State.Name & County.Name, COUNTY_FIPS
keep_epa_cols <- c("COUNTY_FIPS", "State.Abbreviation", "County.Name")
epa_counties <- epa_counties[ , keep_epa_cols]
epa_counties

```


# Generate county adjacency file


```{r}

setwd('__ PATH HERE __')

vertical_county_adj <- read.csv("./TRACT_AHRQ/county_adjacency.csv", header = TRUE, stringsAsFactors = FALSE)
head(vertical_county_adj)

horiz_county_adj <-  subset(vertical_county_adj, select = -c(V1,V3))
names(horiz_county_adj)

# Rename columns
long_adj <- horiz_county_adj %>% 
        rename("FIPS_key" = "V2",
               "neighbors" = "V4")
long_adj

# Fill NAs in FIPS_key column to get into 'long' format
df_filled <- long_adj %>%
  mutate(FIPS_keys_filled = ifelse(!is.na(FIPS_key), FIPS_key, NA)) %>%
  fill(FIPS_keys_filled, .direction = "down") %>%
  select(-FIPS_key) %>%
  rename(FIPS_key = FIPS_keys_filled)

#df_filled
df <- df_filled

# Turn long --> WIDE format. We want wide format.
# Convert the dataframe to a named list (dictionary)
df_dict <- df %>%
  mutate(neighbors = map(neighbors, as.integer)) %>%
  group_by(FIPS_key) %>%
  summarise(neighbors = list(unlist(neighbors))) %>%
  deframe()

# Iterate through the df_dict and remove entries in the value list that match the key
for (key in names(df_dict)) {
  value_list <- df_dict[[key]]
  value_list <- value_list[!value_list %in% key]
  df_dict[[key]] <- value_list
}

# Print the updated dictionary
print(df_dict)


#######
# Convert dict to dataframe
#######

df <- df_dict %>%
  enframe(name = "FIPS_key", value = "neighbors") %>%
  unnest(neighbors)

# Pivot the dataframe to get separate columns for each neighbor
FIPS_adj_final <- df %>%
  group_by(FIPS_key) %>%
  mutate(neighbor_num = row_number()) %>%
  pivot_wider(names_from = neighbor_num, values_from = neighbors, names_prefix = "neighbor_") %>%
  ungroup()

# Print the resulting dataframe
print(FIPS_adj_final)

write.csv(FIPS_adj_final, file='./TRACT_AHRQ/county_adjacency_clean.csv', row.names = FALSE)


```


#############################################
Below is AQI processing
#############################################
# Convert AQI From long -> wide format (wide has no duplicate FIPS county numbers in 1st column)


```{r}

# US Counties and neighbors file from US Census Bureau
# File link: https://www.census.gov/geographies/reference-files/2010/geo/county-adjacency.html
# The file layout description is given here:
# https://www.census.gov/programs-surveys/geography/technical-documentation/records-layout/county-adjacency-record-layout.html
# Convert tab delimeted txt file to csv file

# aqi_remove_cols <- c() # c("State")
# aqi_keep_cols <- names(aqi_total)[! names(aqi_total) %in% aqi_remove_cols]

# Keep only 'aqi_keep_cols'
aqi_kept_feats <- aqi_total # [, ..aqi_keep_cols]
aqi_kept_feats
# Remove all special chars in "County" column
# aqi_kept_feats$County = str_replace_all(aqi_kept_feats$County, "[^[:alnum:]]", "") 
# Don't do, '-' will turn into no space, make difficult for crosswalk.
# Convert to upper: for character matching on merge.
#aqi_kept_feats$County = toupper(aqi_kept_feats$County)
# Convert State column to abbrevs, not full name.
aqi_kept_feats$State = state.abb[match(aqi_kept_feats$State, state.name)]
aqi_kept_feats

```



# READ COUNTY FIPS list for AQI processing

```{r}
#############################
# US Counties and neighbors file from US Census Bureau
# File link: https://www.census.gov/geographies/reference-files/2010/geo/county-adjacency.html
# The file layout description is given here:
# https://www.census.gov/programs-surveys/geography/technical-documentation/records-layout/county-adjacency-record-layout.html
# Convert tab delimeted txt file to csv file

# Load the required library
## library(readr)
# Read the tab-separated file
## df <- read.table('county_adjacency.txt', sep='\t', header=FALSE)
# Write the DataFrame to a CSV file
## write.csv(df, 'county_adjacency.csv', row.names=FALSE)
# Note county_adjacency CSV Column names:
# Column Name  || 	Column Description
# County Name:	2010 State and County Name
# County GEOID:	2010 State and County FIPS Codes
# Neighbor Name: 	2010 State and County name of each neighboring county or county equivalent
# Neighbor GEOID: 2010 State and County FIPS Codes of each neighboring county or county equivalent

# Convert csv file to appropriate neighbor csv format
# Read the CSV file with data in the first format
setwd('__ PATH HERE __')

vertical_county_adj <- read.csv("./TRACT_AHRQ/county_adjacency.csv", header = TRUE, stringsAsFactors = FALSE)
head(vertical_county_adj)

# 1.) Make wide format: (County FIPS <-> county name <-> state abbrev)
# So keep: V1, V2
# wide_county_fips_to_name <- subset(vertical_county_adj, select = -c(V3,V4))
# head(wide_county_fips_to_name)
# # Split V1 <chr> column on "," and make new state column
# wide_county_fips_to_name[c('County_Name', 'State_Abbrev')] <- str_split_fixed(wide_county_fips_to_name$V1, ',', 2)
# wide_county_fips_to_name <- wide_county_fips_to_name[c('V2', 'County_Name', 'State_Abbrev')] # Set column names
# colnames(wide_county_fips_to_name)[colnames(wide_county_fips_to_name) == "V2"] ="County_FIPS" # Rename V2 to County_FIPS
```


# Missing AQI data calculations

# Check: do all counties in 'ck_counties_2,' the full FIPS list, have representation in 'ck_counties_1' ?
- As we see in Georgia, "GA," no... there are 159 total counties in GA (shown in ck_counties_2)
... however, ck_counties_1 only has AQI data for 32 of these 159 counties (at some point in time from 2009-2020).
## RESULT: Spatial missingness for GA: 32 / 159 present (i.e. 20.1% present), 
## i.e. there is complete temporal missingness for 127 counties in GA (i.e. no AQI data was ever collected for these counties from 2009-2020)

# Check: overall "Spatial Missingness"
- Note: we will omit those territories without a FIPS number (ex. St. Thomas)
## RESULT: Spatial missingess for all states: 1144 / 3281 counties present (i.e. 35.37% present), 
## This means there is complete temporal missingness for 2090 counties in the USA (i.e. no AQI data was ever collected for these counties from 2009-2020)


```{r}
# First, transform aqi_kept_feats to 'wide' format, showing AQI features from 2009-2020 as columns. Each FIPS is a unique row.
aqi_kept_feats
aqi_wide <- aqi_kept_feats %>%
  pivot_wider(
    id_cols = c(County, State),
    names_from = Year,
    values_from = c(Days.with.AQI, Good.Days, Moderate.Days, 
                    Unhealthy.for.Sensitive.Groups.Days, Unhealthy.Days, 
                    Very.Unhealthy.Days, Hazardous.Days, Max.AQI, X90th.Percentile.AQI, 
                    Median.AQI, Days.CO, Days.NO2, Days.Ozone, Days.PM2.5, Days.PM10),
    names_sep = "."
  ) %>%
  arrange(County)

aqi_wide <- aqi_wide %>% drop_na(State, County)

aqi_wide

# Do right join because wide_county_fips_to_name is ground truth.

# Do string matching: County to County_Name, State to State_Abbrev

# Also Creates new County_FIPS column

epa_counties
AQI_w_FIPS <- right_join(aqi_wide, epa_counties, by=c("County"="County.Name","State"="State.Abbreviation"))
AQI_w_FIPS <- AQI_w_FIPS %>% select(COUNTY_FIPS, everything()) # Move County_FIPS to be first column


res <- (sum(is.na(AQI_w_FIPS$Days.CO.2009))+sum(is.na(AQI_w_FIPS$Days.CO.2010))+sum(is.na(AQI_w_FIPS$Days.CO.2011))+sum(is.na(AQI_w_FIPS$Days.CO.2012))+sum(is.na(AQI_w_FIPS$Days.CO.2013))+sum(is.na(AQI_w_FIPS$Days.CO.2014))+sum(is.na(AQI_w_FIPS$Days.CO.2015))+sum(is.na(AQI_w_FIPS$Days.CO.2016))+sum(is.na(AQI_w_FIPS$Days.CO.2017))+sum(is.na(AQI_w_FIPS$Days.CO.2018))+sum(is.na(AQI_w_FIPS$Days.CO.2019))+sum(is.na(AQI_w_FIPS$Days.CO.2020))) / 42653


```


```{r}

prefix_list <- c("Days.with.AQI", "Good.Days", "Moderate.Days", "Unhealthy.for.Sensitive.Groups.Days", "Unhealthy.Days", "Very.Unhealthy.Days", "Hazardous.Days", "Max.AQI", "X90th.Percentile.AQI", "Median.AQI", "Days.CO", "Days.NO2", "Days.Ozone", "Days.PM2.5", "Days.PM10")


aqi_long <- AQI_w_FIPS %>%
  pivot_longer(
    cols = -c(County, State),
    names_to = c(".value", "Year"),
    names_pattern = "^(.+)\\.(\\d{4})$",
    values_drop_na = FALSE
  ) %>%
  select(County, State, Year, any_of(prefix_list)) %>%
  arrange(County)

nrow(aqi_long)
sum(is.na(aqi_long$Good.Days))


# Missing: 27064 / 42653 = 63 % missing 
res <- (sum(is.na(AQI_w_FIPS$Days.with.AQI.2009))+sum(is.na(AQI_w_FIPS$Days.with.AQI.2010))+sum(is.na(AQI_w_FIPS$Days.with.AQI.2011))+sum(is.na(AQI_w_FIPS$Days.with.AQI.2012))+sum(is.na(AQI_w_FIPS$Days.with.AQI.2013))+sum(is.na(AQI_w_FIPS$Days.with.AQI.2014))+sum(is.na(AQI_w_FIPS$Days.with.AQI.2015))+sum(is.na(AQI_w_FIPS$Days.with.AQI.2016))+sum(is.na(AQI_w_FIPS$Days.with.AQI.2017))+sum(is.na(AQI_w_FIPS$Days.with.AQI.2018))+sum(is.na(AQI_w_FIPS$Days.with.AQI.2019))+sum(is.na(AQI_w_FIPS$Days.with.AQI.2020))) / 42653


na_count <-sapply(aqi_long, function(y) sum(length(which(is.na(y)))))

missing_country <- data.frame(na_count) / 42653
missing_country # Shows MISSINGNESS. Ex. 67% missing for Days.with.AQI.2009.



# sum cols

```

# Total country AQI data: 
```{r}

setwd('__ PATH HERE __')

write.csv(AQI_w_FIPS, "totalCountry_AQI_by_FIPS_beforeimputation.csv", row.names=FALSE)

```

# Georgia (GA) only
Using GA as an example.
```{r}
state_AQI_w_FIPS <- AQI_w_FIPS[AQI_w_FIPS$State == "GA", ]
state_AQI_w_FIPS

write.csv(state_AQI_w_FIPS, "GAstate_AQI_by_FIPS_beforeimputation.csv", row.names=FALSE)
```

# Map: BEFORE IMPUTATION 
# Mapping with usmap library: https://stackoverflow.com/questions/63004172/putting-values-on-a-county-map-in-r
```{r}
d   <- us_map("counties")
d   <- d[d$abbr == "GA",]
GAc <- lapply(split(d, d$county), function(x) st_polygon(list(cbind(x$x, x$y))))
GA  <- st_sfc(GAc, crs = usmap_crs()@projargs)
GA  <- st_sf(data.frame(fips = unique(d$fips), county = names(GAc), geometry = GA))



GA_aqi_2009 <- subset(state_AQI_w_FIPS, select = c("COUNTY_FIPS", "Days.PM2.5.2010"))

#GA <- dplyr::right_join(GA, GA_aqi_2009, by = c("fips" = "COUNTY_FIPS"))
# Put 0s for all rows with NAs
#GA[is.na(GA)] <- 0
#GA$centroids <- st_centroid(GA$geometry)
#GA$Days.with.AQI.2009
# Change col names

colnames(GA_aqi_2009) <-  c("fips", "Days.PM2.5.2010")


plot_usmap( data = GA_aqi_2009, values = "Days.PM2.5.2010", "counties", include = c("GA"), color="black") +  
    labs(title="")+  
    scale_fill_continuous(low = "#56B1F7", high = "#132B43", name="2010: Days PM2.5 Main Poll.", label=scales::comma)+  
    theme(plot.background=element_rect(), legend.position="right") +
    theme(plot.background = element_rect(color=NA, fill = "white"),
             panel.background = element_rect(color=NA, fill = "white"))


```


# Use cell above to show plot of "BEFORE IMPUTATION" missing feat distribution
... replace Days.with.AQI.2009 with _desired feat_
```{r}
# Here, you can plot other feats BEFORE IMPUTATION


```


# Spatial AQS Imputation
impute upon *AQI_w_FIPS*, using county_adj as the guide to know which FIPS are neighbors.
For all imputation approaches, we aim to reach a full matrix of AQI features for all counties. 
The full matrix is required in order to have values for each year for each location, as the 'baseline year' feature experiments may require AQI features from a single year in a county, instead of averaging a county AQI features over years 2009-2020.

```{r}
# Read in the FIPS adjacency file (created above)
setwd('__ PATH HERE __')


county_adj <- read.csv(file='./TRACT_AHRQ/county_adjacency_clean.csv')
AQI_w_FIPS <- read.csv(file='totalCountry_AQI_by_FIPS_beforeimputation.csv') # National county imputation.

############ 1.1 Simple spatial imputation (iterate & repeat until fully imputed.)
# (1.1) We use mean for spatial imputation because we assume the features have a normal dist among neighbors. 

# Below, we will do spatial imputation. 
# This means, for a given FIPS (i.e. row): if a missing value exists, 
imp_1_AQI_by_FIPS <- AQI_w_FIPS 
cols <- setdiff(names(AQI_w_FIPS), c("COUNTY_FIPS", "County", "State"))
  
impute_AQI_iterate <- function(imp_1_AQI_by_FIPS, cols) {
  failed_imp <- 0 # To count num where neighbors didn't have any vals for that feature to impute.
  # Iterate across columns
  for (i in seq_along(cols)){
    #prevcol <- cols[i-1]
    thiscol <- cols[i]
    curr_year <- sub(".*\\.(\\d+)$", "\\1", thiscol)
    # This loop goes down the column
    for(j in seq_along(imp_1_AQI_by_FIPS[[thiscol]])){
      cell_val <- imp_1_AQI_by_FIPS[j, thiscol][1] 
      if(is.na(cell_val)){
        #print(cell_val)
        curr_FIPS <- imp_1_AQI_by_FIPS[j, "COUNTY_FIPS"]
        #print(curr_FIPS)
        neighs <- as.list(county_adj[county_adj$FIPS_key == curr_FIPS,])
        neighs <- unname(neighs) # Removes column names from neighbor list.
        if(length(neighs) > 0){
          neighs <- as.list( neighs[2 : length(neighs)] ) # Drop first list elmnt (i.e. the key)
        }
        #print(neighs)
        # Now take mean of neighbor feat vals: for 'thiscol'
        imp_cell <- imp_1_AQI_by_FIPS[imp_1_AQI_by_FIPS$COUNTY_FIPS %in% neighs,][thiscol] 
        imp_cell <- imp_cell[!is.na(imp_cell)]
        if(length(imp_cell) > 0 ){
          imp_cell <- mean(imp_cell)
        }
        
  
        # If NA, then imp_cell length is 0.
        if(length(imp_cell) > 0){
          imp_1_AQI_by_FIPS[j, thiscol] <- imp_cell
        }
        else{
          failed_imp = failed_imp + 1
        }
        #print(imp_cell)
      }
    }
  }
  
  return(imp_1_AQI_by_FIPS)
} # End function

# Track num left to impute (for each feature)
imp_runs = 3

cols_num_still_NA <- data.frame(matrix(ncol = length(cols), nrow = (imp_runs+1) ))
colnames(cols_num_still_NA) <- cols
# Get initial number needed to impute (before ANY imputation).
num_NAs_left <- sapply(imp_1_AQI_by_FIPS, function(x) sum(is.na(x)))
cols_num_still_NA[1,] <- num_NAs_left  # Add row for num NAs in each column of 'imp_1_AQI_by_FIPS'


# Perform imputation over 'imp_runs' num of iterations 
for(i in 1:imp_runs){
  # run imp
  imp_1_AQI_by_FIPS <- impute_AQI_iterate(imp_1_AQI_by_FIPS, cols)
  print(sum(is.na(imp_1_AQI_by_FIPS)))
  
  # If after 1st iterationAdd row for num NAs in each column of 'imp_1_AQI_by_FIPS'
  num_NAs_left <- sapply(imp_1_AQI_by_FIPS, function(x) sum(is.na(x)))
  cols_num_still_NA[i + 1,] <- num_NAs_left
}
  

# Plot: how many LEFT to be imputed (in each feature column)
cols_num_still_NA # num iterations = nrows -1 
# Result of imp: imp_1_AQI_by_FIPS


# Temporarily remove spatial identifiers for renaming columns
cols <- setdiff(names(imp_1_AQI_by_FIPS), c("COUNTY_FIPS", "County", "State"))
imp_1_AQI_by_FIPS <- subset(imp_1_AQI_by_FIPS, select = cols)

# Rename all feats to indicate SPATIAl imp was done:
colnames(imp_1_AQI_by_FIPS) <- paste("spatialIMP", colnames(imp_1_AQI_by_FIPS), sep = ".")

# Bring back in c("COUNTY_FIPS", "County", "State")
COUNTY_FIPS <- AQI_w_FIPS$COUNTY_FIPS
County <- AQI_w_FIPS$County
State <- AQI_w_FIPS$State
imp_1_AQI_by_FIPS <- cbind(imp_1_AQI_by_FIPS, COUNTY_FIPS, County, State ) 

sum(is.na(imp_1_AQI_by_FIPS)) # Ideally until no NAs. 
write.csv(imp_1_AQI_by_FIPS, file="totalCountry_final_spatial_imp_1.csv", row.names = FALSE )
```

# After national county imputation, check which counties still have NAs:
```{r}
imp_1_AQI_by_FIPS

```


```{r}
d   <- us_map("counties")
d   <- d[d$abbr == "GA",]
GAc <- lapply(split(d, d$county), function(x) st_polygon(list(cbind(x$x, x$y))))
GA  <- st_sfc(GAc, crs = usmap_crs()@projargs)
GA  <- st_sf(data.frame(fips = unique(d$fips), county = names(GAc), geometry = GA))


GA_aqi_2009 <- subset(imp_1_AQI_by_FIPS, select = c("COUNTY_FIPS", "spatialIMP.Days.PM2.5.2010"))

#GA <- dplyr::right_join(GA, GA_aqi_2009, by = c("fips" = "COUNTY_FIPS"))
# Put 0s for all rows with NAs
#GA[is.na(GA)] <- 0
#GA$centroids <- st_centroid(GA$geometry)
#GA$Days.with.AQI.2009
# Change col names

colnames(GA_aqi_2009) <-  c("fips", "Days.PM2.5.2010")


plot_usmap( data = GA_aqi_2009, values = "Days.PM2.5.2010", "counties", include = c("GA"), color="black") +  
    labs(title="")+  
    scale_fill_continuous(low = "#56B1F7", high = "#132B43", name="2010: Days PM2.5 Main Poll.", label=scales::comma)+  
    theme(plot.background=element_rect(), legend.position="right") + 
    theme(plot.background = element_rect(color=NA, fill = "white"),
             panel.background = element_rect(color=NA, fill = "white"))

```

# PLOT: (pick 1 year) Show % of NAs left per feature column - after k iterations of spatial imputation. 
# Note: This is only imputation within the state. 
```{r}

# For year 2009: 
# Plot w raw vals first

year = "2009"

plt_gs_NAs <- cols_num_still_NA[ , grepl( year , names( cols_num_still_NA ) ) ]
# Plot w percent NAs (cols in cols_num_still_NA / nrow(imp_1_AQI_by_FIPS))

matplot(plt_gs_NAs, type = "b",pch=1,col = 1:ncol(plt_gs_NAs))
legend("topright", legend = 1:ncol(plt_gs_NAs), col=1:ncol(plt_gs_NAs), pch=1)


```


# Baseline: mean feature imputation
```{r}
AQI_w_FIPS

cols <- setdiff(names(AQI_w_FIPS), c("COUNTY_FIPS", "County", "State"))
imputed_dataframe <- subset(AQI_w_FIPS, select = cols)
for (col in names(imputed_dataframe)) {
    if (is.numeric(imputed_dataframe[[col]])) {
      mean_value <- mean(imputed_dataframe[[col]], na.rm = TRUE)
      imputed_dataframe[[col]][is.na(imputed_dataframe[[col]])] <- mean_value
    }
}



# Temporarily remove spatial identifiers for renaming columns
cols <- setdiff(names(imputed_dataframe), c("COUNTY_FIPS", "County", "State"))
imputed_dataframe <- subset(imputed_dataframe, select = cols)

# Rename all feats to indicate med imp was done:
colnames(imputed_dataframe) <- paste("meanIMP", colnames(imputed_dataframe), sep = ".")

# Bring back in c("COUNTY_FIPS", "County", "State")
COUNTY_FIPS <- AQI_w_FIPS$COUNTY_FIPS
County <- AQI_w_FIPS$County
State <- AQI_w_FIPS$State
imputed_dataframe <- cbind(imputed_dataframe, COUNTY_FIPS, County, State ) 




write.csv(imputed_dataframe, file="EPA_AQS_mean_imp.csv", row.names = FALSE )

```

# Baseline: median feature imputation
```{r}
# imputing remaining NAs via median of column.
# Impute NAs with column medians (ignoring NAs when calculating median)

cols <- setdiff(names(AQI_w_FIPS), c("COUNTY_FIPS", "County", "State"))
imputed_dataframe <- subset(AQI_w_FIPS, select = cols)
for (col in names(imputed_dataframe)) {
    if (is.numeric(imputed_dataframe[[col]])) {
      median_value <- median(imputed_dataframe[[col]], na.rm = TRUE)
      imputed_dataframe[[col]][is.na(imputed_dataframe[[col]])] <- median_value
    }
}






# Temporarily remove spatial identifiers for renaming columns
cols <- setdiff(names(imputed_dataframe), c("COUNTY_FIPS", "County", "State"))
imputed_dataframe <- subset(imputed_dataframe, select = cols)

# Rename all feats to indicate med imp was done:
colnames(imputed_dataframe) <- paste("medianIMP", colnames(imputed_dataframe), sep = ".")

# Bring back in c("COUNTY_FIPS", "County", "State")
COUNTY_FIPS <- AQI_w_FIPS$COUNTY_FIPS
County <- AQI_w_FIPS$County
State <- AQI_w_FIPS$State
imputed_dataframe <- cbind(imputed_dataframe, COUNTY_FIPS, County, State ) 



 
write.csv(imputed_dataframe, file="EPA_AQS_median_imp.csv", row.names = FALSE )

imputed_dataframe$medianIMP.Good.Days.2010

# Plot Median for: Good.Days.2010

d   <- us_map("counties")
d   <- d[d$abbr == "GA",]
GAc <- lapply(split(d, d$county), function(x) st_polygon(list(cbind(x$x, x$y))))
GA  <- st_sfc(GAc, crs = usmap_crs()@projargs)
GA  <- st_sf(data.frame(fips = unique(d$fips), county = names(GAc), geometry = GA))



GA_aqi_2009 <- subset(imputed_dataframe, select = c("COUNTY_FIPS", "medianIMP.Days.PM2.5.2010"))

#GA <- dplyr::right_join(GA, GA_aqi_2009, by = c("fips" = "COUNTY_FIPS"))
# Put 0s for all rows with NAs
#GA[is.na(GA)] <- 0
#GA$centroids <- st_centroid(GA$geometry)
#GA$Days.with.AQI.2009
# Change col names

colnames(GA_aqi_2009) <-  c("fips", "Days.PM2.5.2010")


plot_usmap( data = GA_aqi_2009, values = "Days.PM2.5.2010", "counties", include = c("GA"), color="black") +  
    labs(title="")+  
    scale_fill_continuous(low = "#56B1F7", high = "#132B43", name="2010: Days PM2.5 Main Poll.", label=scales::comma)+  
    theme(plot.background=element_rect(), legend.position="right")  +
    theme(plot.background = element_rect(color=NA, fill = "white"),
             panel.background = element_rect(color=NA, fill = "white"))

```
